---
title: "Pollination Experiment in CO"
author: "Emma"
date: "2024-11-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
remove(list = ls())
set.seed(459813)
# setwd(dir = "Programs/")
```


Load Packages
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggforce) 
library(patchwork)
library(lme4)
library(car)
library(forcats)
library(DHARMa)
library(MuMIn)
library(emmeans)
library(ggpubr)
library(ggeffects)
library(performance)
library(arm)
```


Load data
```{r}
meta <- read.csv("Raw_Data/Data/Pollination_Experiment.csv", header = TRUE)
data <- read.csv("Raw_Data/Data/Pollination_Experiment_Seeds.csv", header = TRUE)
sex_ratio <- read.csv("Raw_Data/Data/Pollen_Deposition.csv")
```

Format sex_ratio dataframe to long format
```{r}
sex_ratio1 <- sex_ratio %>% 
  dplyr::select(Site:Sex, SR_Herm_A, SR_Herm_B, SR_Herm_C, SR_Herm_D) %>% 
  pivot_longer(cols = starts_with(c("SR_Herm")),
               names_to = c("week"),
               names_prefix = c("SR_Herm_"),
               values_to = c("Herm_Count")) 
  
sex_ratio2 <- sex_ratio %>% 
  dplyr::select(c(Site:Sex, SR_Fem_A, SR_Fem_B, SR_Fem_C, SR_Fem_D)) %>% 
  pivot_longer(cols = starts_with(c("SR_Fem")),
               names_to = c("week"),
               names_prefix = c("SR_Fem_"),
               values_to = c("Fem_Count")) 

sex_ratio_3 <- merge(sex_ratio1,sex_ratio2, by = c("Site", "Population", "Plot",
                                                     "Plant.ID", "TP", "Sex", "week"), 
                       all.y = TRUE)

sex_ratio_all <- sex_ratio_3 %>% 
  mutate(true_HermCount = if_else(Sex == "H", Herm_Count-1, Herm_Count)) %>% 
  mutate(true_FemCount = if_else(Sex == "F", Fem_Count-1, Fem_Count)) %>% 
  mutate(micro_SR = true_HermCount/(true_FemCount+true_HermCount),
         density = (true_HermCount + true_FemCount + 1) / pi) %>% 
  filter(week == "B") %>% 
  drop_na()


```


Combine dataframes
```{r}
meta2 <- meta %>% mutate(POP_code = ifelse(Population == "East Krummholz", "EK", "WK"))
meta2$ID <- toupper(paste0(meta2$POP_code,meta2$Plant.ID))

data$ID <- toupper(data$ID)
data2<- data %>% 
  mutate(Treatment = case_when(Color == "G" ~ "Outcrossed",
                                              Color == "R" ~ "Selfed",
                                              Color == "B" ~ "No Pollen",
                                              Color == "O" ~ "Open Pollinated"))

data3 <- merge(meta2, data2, by = "ID", all.y = TRUE)

data_all <- merge(data3, sex_ratio_all, by = c("Plant.ID", "Population", "Site", "Plot", "TP", "Sex"))

```


Calculated Variables
```{r}
data_all <- data_all %>% 
  mutate(Germination_rate = data_all$Germinated / data_all$Total_Seeds_end) %>% 
  mutate(Germination_rate = replace_na(Germination_rate, 0))

data_all$viable_seed <- round(data_all$Fruit * data_all$Seed_number * data_all$Germination_rate)

```

Subset dataframe to just include treatments that fruited and remove mix sex. Remove female flower that set fruit in the no pollen treatment.
```{r}
data_all <- data_all %>% 
  filter(Sex != "mix") %>% 
  filter(!(Treatment == "No Pollen" & Sex == "F" & Fruit == 1)) %>% 
  mutate(Fruit_char = case_when(Fruit == 1 ~ "Fruit",
                                Fruit == 0 ~ "No Fruit"),
         Population = case_when(Population == "West Knoll" ~ "Low Hermaphrodite",
                                Population == "East Krummholz" ~ "High Hermaphrodite"))

data_seeds <- data_all %>% 
  filter(Seed_number != 0) %>% 
  drop_na(Population)

# Total observations
meta %>% 
  group_by(Sex, Population) %>% 
  summarise(n = n_distinct(Plant.ID))

data_all %>% 
  group_by(Sex, Population) %>% 
  summarise(n = n_distinct(Plant.ID))

data_all %>% 
  filter(Fruit == 1) %>% 
  summarise(n=n())

data_all %>% 
  filter(Fruit == 1) %>% 
  summarise(seeds=sum(Seeds_plated))

```



## Fruit Production
```{r}
data_all$Treatment <- factor(data_all$Treatment, levels = c("Open Pollinated", "Outcrossed", "Selfed", "No Pollen"))
data_all$Sex <- as.factor(data_all$Sex)
  

fruit.m <- glm(Fruit ~ Sex * Treatment+ Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount + Population, data = data_all, family = "binomial")

summary(fruit.m)
Anova(fruit.m)
r.squaredGLMM(fruit.m)

#Check Overdispersion
check_overdispersion(fruit.m)

# Model diagnostics
fruit_res <- simulateResiduals(fruit.m)
plot(fruit_res)


emmeans(fruit.m, specs = pairwise ~ Treatment*Sex, adjust="tukey")


fruit_plot <- data_all %>% 
  mutate(Sex2 = if_else(Sex == "F", "Female", "Hermaphrodite"))

(fruit_plot1 <- ggplot(data = fruit_plot, aes(x = Treatment, fill = fct_rev(Fruit_char))) +
  geom_bar(position = "fill") +
  labs(x = "Pollination Treatment", 
       y = "Fruit Set Proportion") +
  theme_classic() +
  scale_fill_manual(values = c("grey", "black")) +
  facet_wrap(~ Sex2, scales = "free_x") +
  theme(legend.title = element_blank(),
        legend.position = "right",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))


```

Inbreeding Depression Figure
```{r}
# Plot effect of micro sex ratio on inbreeding depression
predict1 <- ggpredict(fruit.m, terms = c("true_HermCount [all]", "Treatment", "Sex")) %>% 
  filter(facet == "H" & (group == "Outcrossed" | group == "Selfed"))


predict_ID <- as.data.frame(predict1) %>% 
  dplyr::select(-facet, -std.error) %>% 
  pivot_wider(names_from = group, 
              values_from = c(predicted, conf.low, conf.high),
              names_sep = ".") %>% 
  mutate(ID = (predicted.Outcrossed-predicted.Selfed)/predicted.Outcrossed)

# Getting confidence intervals for inbreeding depression calculated from predictions
library(arm)

sim_model <- sim(fruit.m, n.sims = 1000)

ID_list <- list()

for (i in c("Outcrossed", "Selfed")) {
  newdata_low <- data.frame(
  Sex = factor("H",levels = levels(data_all$Sex)),
  Treatment = factor(i, levels(data_all$Treatment)),
  true_HermCount = seq(min(data_all$true_HermCount), max(data_all$true_HermCount), length.out = 100),
  true_FemCount = median(data_all$true_FemCount),
  Population = "Low Hermaphrodite")

newdata_high <- newdata_low
newdata_high$Population <- "High Hermaphrodite"

newdata <- rbind(newdata_high, newdata_low)

df_name <- i

ID_list[[df_name]] <- newdata

}

# Matrix of model coefficients: sims x predictors
sim_coefs <- coef(sim_model)

# Design matrix for new data
X_out <- model.matrix(~ Sex * Treatment+ Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount + Population, data = ID_list$Outcrossed)

X_self <- model.matrix(~ Sex * Treatment+ Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount + Population, data = ID_list$Selfed)


# Multiply each simulation of coefs by design matrix to get linear predictors
pred_out_mat <- plogis(sim_coefs %*% t(X_out))
pred_self_mat <- plogis(sim_coefs %*% t(X_self))

# Now compute inbreeding depression
id_matrix <- (pred_out_mat - pred_self_mat) / pred_out_mat

id_mean <- apply(id_matrix, 2, mean)
id_lower <- apply(id_matrix, 2, quantile, probs = 0.025)
id_upper <- apply(id_matrix, 2, quantile, probs = 0.975)

# Put it into a data frame for plotting
id_df <- data.frame(
  true_HermCount = ID_list$Outcrossed$true_HermCount,
  ID_mean = id_mean,
  ID_lower = id_lower,
  ID_upper = id_upper
)


# Make plots with model predictions and ID
data_ID <- data_all %>% 
  filter(Sex == "H" & (Treatment == "Outcrossed" | Treatment == "Selfed"))


(ID_plot1 <- ggplot(data = predict1) +
  geom_line(aes(x=x, y=predicted, color = group), linewidth = 1) +
  geom_ribbon(aes(x=x, ymin = conf.low, ymax = conf.high, group = group), alpha = 0.2) +
  geom_jitter(data = data_ID, aes(x = true_HermCount, y = Fruit, color = Treatment), 
              alpha = 0.2, height = 0.05) +
  labs(x = "Hermaphrodite Number", y = "Fruit Set Proportion",
       color = "") +
  scale_color_manual(values = c("#ADFF2F", "#008B00"))+
  theme_classic()+
  theme(legend.position = "top",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")))
  
(ID_plot2 <- ggplot() +
  geom_smooth(data = predict_ID, aes(x=x, y=ID), linewidth = 1, se = FALSE, color = "grey50") +
  geom_ribbon(data = id_df, aes(x=true_HermCount, ymin = ID_lower, ymax = ID_upper), alpha = 0.2) +
  labs(x = "Hermaphrodite Number", y = "Inbreeding Depression") +
  theme_classic())

(ID_plot <- ggarrange(ID_plot1, ID_plot2, nrow = 1, ncol = 2, labels = c("A", "B"), widths = c(0.60,0.40)))

ggsave(ID_plot, file = "./Figures/ID_plot.png", width = 8, height = 4, units = "in", dpi = 300)
```

Pollen Limitation figure
```{r}
# Plot of pollen limitation
predict2 <- ggpredict(fruit.m, terms = c("true_HermCount [all]", "Treatment", "Sex")) %>%
  filter(group == "Outcrossed" | group == "Open Pollinated")  


predict_PL <- as.data.frame(predict2) %>% 
  dplyr::select(-std.error) %>% 
  pivot_wider(names_from = group, 
              values_from = c(predicted, conf.low, conf.high),
              names_sep = ".") %>% 
  rename(predicted.Open = 'predicted.Open Pollinated',
         conf.low.Open = 'conf.low.Open Pollinated',
         conf.high.Open = 'conf.high.Open Pollinated') %>% 
  mutate(PL = log(predicted.Outcrossed/predicted.Open))

# Calculate confidence intervals with delta method for pollen limitation
predict_F <- predict2 %>% 
  filter(facet == "F")

predict_H <- predict2 %>% 
  filter(facet == "H")

data_PL_F <- data_all %>% 
  filter(Sex == "F" & (Treatment == "Outcrossed" | Treatment == "Open Pollinated"))

data_PL_H <- data_all %>% 
  filter(Sex == "H" & (Treatment == "Outcrossed" | Treatment == "Open Pollinated"))

# Getting confidence intervals for inbreeding depression calculated from predictions
sim_model <- sim(fruit.m, n.sims = 1000)

PL_list <- list()

for (sex in c("F", "H")) {
  for (trt in c("Outcrossed", "Open Pollinated")) {
    newdata <- data.frame(
    Sex = factor(sex,levels = levels(data_all$Sex)),
    Treatment = factor(trt, levels(data_all$Treatment)),
   true_HermCount = seq(min(data_all$true_HermCount), max(data_all$true_HermCount), length.out = 100),
    true_FemCount = median(data_all$true_FemCount),
    Population = rep(c("Low Hermaphrodite", "High Hermaphrodite"), times = 50))
    
    df_name <- paste0(trt,"_", sex)
    PL_list[[df_name]] <- newdata

  }
}

PL_Outcrossed <- rbind(PL_list$Outcrossed_F, PL_list$Outcrossed_H)
PL_Open <- rbind(PL_list$'Open Pollinated_F', PL_list$'Open Pollinated_H')

# Matrix of model coefficients: sims x predictors
sim_coefs <- coef(sim_model)

# Design matrix for new data
X_out <- model.matrix(~ Sex * Treatment+ Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount + Population, data = PL_Outcrossed)

X_open <- model.matrix(~ Sex * Treatment+ Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount + Population, data = PL_Open)


# Multiply each simulation of coefs by design matrix to get linear predictors
pred_out_mat <- plogis(sim_coefs %*% t(X_out))
pred_open_mat <- plogis(sim_coefs %*% t(X_open))

# Now compute inbreeding depression
pl_matrix <- log(pred_out_mat/pred_open_mat)

pl_mean <- apply(pl_matrix, 2, mean)
pl_lower <- apply(pl_matrix, 2, quantile, probs = 0.025)
pl_upper <- apply(pl_matrix, 2, quantile, probs = 0.975)



# Put it into a data frame for plotting
PL_df <- data.frame(
  true_HermCount = PL_Open$true_HermCount,
  Sex = PL_Open$Sex,
  PL_mean = pl_mean,
  PL_lower = pl_lower,
  PL_upper = pl_upper)



(PL_F_plot <- ggplot() +
  geom_line(data = predict_F, aes(x=x, y=predicted, color = group), size = 1) +
  geom_ribbon(data = predict_F, 
              aes(x=x, ymin = conf.low, ymax = conf.high, group = group, fill = group), 
              alpha = 0.2) +
  geom_jitter(data = data_PL_F, aes(x = true_HermCount, y = Fruit, color = Treatment), 
              alpha = 0.6, height = 0.05) +
  labs(x = "Hermaphrodite Neighbors", y = "Fruit Set \nProportion", 
       title ="Female") +
  scale_color_manual(values = c("grey50", "black"))+
  scale_fill_manual(values = c("grey50", "black"))+
  theme_classic() +
  theme(legend.position = "right",
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")))

(PL_H_plot <- ggplot() +
  geom_line(data = predict_H, aes(x=x, y=predicted, color = group), size = 1) +
  geom_ribbon(data = predict_H, 
              aes(x=x, ymin = conf.low, ymax = conf.high, group = group, fill = group), 
              alpha = 0.2) +
  geom_jitter(data = data_PL_H, aes(x = true_HermCount, y = Fruit, color = Treatment), 
              alpha = 0.6, height = 0.05) +
  labs(x = "Hermaphrodite Neighbors", y = "",
       title = "Hermaphrodite") +
  scale_color_manual(values = c("grey50", "black"))+
  scale_fill_manual(values = c("grey50", "black"))+
  theme_classic()+
  theme(legend.position = "right",
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")))



(PL_plot <- ggplot() +
  geom_smooth(data = predict_PL, aes(x=x, y=PL, color = facet), size = 1, se = FALSE) +
  geom_ribbon(data = PL_df, aes(x=true_HermCount, ymin = PL_lower, ymax = PL_upper, group = Sex, fill = Sex), alpha = 0.2) +
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  labs(x = "Hermaphrodite Neighbors", y = "Pollen \nLimitation",
       color = "Sex") +
  theme_classic() +
  theme(legend.position = "bottom"))

(PL_plot_pannel_1 <- ggarrange(ggarrange(PL_F_plot, PL_H_plot, nrow = 1, 
                               common.legend = TRUE, legend = "bottom", 
                               labels = c("C", "D")), PL_plot, nrow = 1, labels = c("", "E"), widths = c(0.65, 0.35)))


```

## Female advantage in fruitset plot
```{r}
# Female advantage - relative fruit set of females to hermaphrodites

predict_FA <- as.data.frame(predict2) %>% 
  dplyr::select(-std.error) %>% 
  pivot_wider(names_from = facet, 
              values_from = c(predicted, conf.low, conf.high),
              names_sep = ".") %>% 
  mutate(FA = log(predicted.F/predicted.H))


# Getting confidence intervals for female advantage calculated from predictions
sim_model <- sim(fruit.m, n.sims = 1000)

FA_list <- list()

for (sex in c("F", "H")) {
  for (trt in c("Outcrossed", "Open Pollinated")) {
    newdata <- data.frame(
    Sex = factor(sex,levels = levels(data_all$Sex)),
    Treatment = factor(trt, levels(data_all$Treatment)),
   true_HermCount = seq(min(data_all$true_HermCount), max(data_all$true_HermCount), length.out = 100),
    true_FemCount = median(data_all$true_FemCount),
    Population = rep(c("Low Hermaphrodite", "High Hermaphrodite"), times = 50))
    
    df_name <- paste0(trt,"_", sex)
    FA_list[[df_name]] <- newdata

  }
}

FA_F <- rbind(PL_list$Outcrossed_F, PL_list$'Open Pollinated_F')
FA_H <- rbind(PL_list$Outcrossed_H, PL_list$'Open Pollinated_H')

# Matrix of model coefficients: sims x predictors
sim_coefs <- coef(sim_model)

# Design matrix for new data
X_F <- model.matrix(~ Sex * Treatment+ Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount + Population, data = FA_F)

X_H <- model.matrix(~ Sex * Treatment+ Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount + Population, data = FA_H)


# Multiply each simulation of coefs by design matrix to get linear predictors
pred_F_mat <- plogis(sim_coefs %*% t(X_F))
pred_H_mat <- plogis(sim_coefs %*% t(X_H))

# Now compute inbreeding depression
FA_matrix <- log(pred_F_mat/pred_H_mat)

FA_mean <- apply(FA_matrix, 2, mean)
FA_lower <- apply(FA_matrix, 2, quantile, probs = 0.025)
FA_upper <- apply(FA_matrix, 2, quantile, probs = 0.975)

# Put it into a data frame for plotting
FA_df <- data.frame(
  true_HermCount = FA_F$true_HermCount,
  Treatment = FA_F$Treatment,
  FA_mean = FA_mean,
  FA_lower = FA_lower,
  FA_upper = FA_upper
)



(FA_plot <- ggplot() +
  geom_smooth(data = predict_FA, aes(x=x, y=FA, color = group), size = 1, se = FALSE) +
  geom_ribbon(data = FA_df, aes(x=true_HermCount, ymin = FA_lower, ymax = FA_upper, group = Treatment, fill = Treatment), alpha = 0.2) +
  scale_color_manual(values = c("grey50", "black"))+
  scale_fill_manual(values = c("grey50", "black"))+ 
  labs(x = "Hermaphrodite Neighbors", y = "Relative \nFemale Advantage",
       color = "Treatment") +
  theme_classic() +
  theme(legend.position = "right",
        legend.title = element_blank()))

(PL_plot_pannel_2 <- ggarrange(PL_plot_pannel_1, FA_plot, nrow = 2, labels = c("", "F")))


```



## Seed Production
```{r}
seeds.m <- glm(Seed_number ~ Sex * Treatment+ Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount + Population, data = data_seeds, family = "poisson")

summary(seeds.m)
Anova(seeds.m)
r.squaredGLMM(seeds.m)


mean_sd <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(seed_mean = mean(Seed_number),
            n = n(),
            seed_se = sd(Seed_number) / (sqrt(n)))

(seed_plot <- ggplot(data = mean_sd, aes(x = Treatment, y = seed_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = seed_mean - seed_se, ymax = seed_mean + seed_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Seed Number") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population, ncol = 2) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position="top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

ggsave(seed_plot, filename = "Figures/Seed_Supp.png", dpi = 300, width = 6, height = 4, units = "in")

(seed_plot2 <- ggplot(data = data_all, aes(x = true_HermCount, y = Seed_number, color = Sex)) +
  geom_point(position = "dodge", alpha = 0.5) +
  geom_smooth(method = "glm", se = T, 
        method.args = list(family = "poisson")) +
  labs(x = "Micro Hermaphrodite Count", y = "Seed Count")+
  theme_classic()+
  facet_wrap(vars(Treatment)) +
  scale_color_manual(values = c("#7A378B", "#66CD00")))

```


## Seed Germination
```{r}

germ.m <- glm(cbind(Germinated, (Total_Seeds_end - Germinated)) ~ Sex * Treatment + Population + Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount, data = data_seeds, family = "binomial")

summary(germ.m)
Anova(germ.m)
r.squaredGLMM(germ.m)


mean_germ <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(germ_mean = mean(Germination_rate),
            n = n(),
            germ_se = sd(Germination_rate) / (sqrt(n)))

(germ_plot <- ggplot(data = mean_germ, aes(x = Treatment, y = germ_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = germ_mean - germ_se, ymax = germ_mean + germ_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Germination Rate") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population, ncol = 2) +
  theme(legend.title = element_blank(),
        legend.position="none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

ggsave(germ_plot, filename = "Figures/Germ_Supp.png", dpi = 300, width = 6, height = 4, units = "in")

# Average germination rate for each treatment
data_seeds %>% group_by(Treatment) %>% 
  summarise(Mean_GermRate = mean(Germination_rate),
            SD_GermRate = sd(Germination_rate),
            Mean_Seed = mean(Seed_number),
            SD_Seed = sd(Seed_number))

```


## Cummulative reproductive output
```{r}

viable_seeds.m <- MASS::glm.nb(viable_seed ~ Sex * Treatment + Population + Sex:true_HermCount + Treatment:true_HermCount + true_FemCount + true_HermCount, data = data_all)

summary(viable_seeds.m)
Anova(viable_seeds.m)
r.squaredGLMM(viable_seeds.m)


emmeans(viable_seeds.m, specs = pairwise ~ Treatment*Sex, adjust="tukey")


fig_germ <- data_all %>% 
  replace(is.na(.), 0) %>% 
  mutate(Figure_vs = Fruit * Seed_number * Germination_rate) %>% 
  mutate(Sex2 = if_else(Sex == "F", "Female", "Hermaphrodite")) %>% 
  drop_na(Figure_vs) %>% 
  group_by(Sex2, Treatment) %>% 
  summarise(viable_mean = mean(Figure_vs),
            n = n(),
            viable_se = sd(Figure_vs) / (sqrt(n)))


(vs_plot <- ggplot(data = fig_germ, aes(x = Treatment, y = viable_mean, fill = Sex2)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = viable_mean - viable_se, ymax = viable_mean + viable_se), 
                position = position_dodge(0.9), width = 0.25) +
  # geom_hline(yintercept = 1.25, linetype = "dotted") +
  labs(x = "Pollination Treatment", y = "Cumulative \nReproductive Output") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~Sex2, scales = "free_x") +
  theme(legend.title = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

ggsave(vs_plot, filename = "Figures/cumulative_plot.png", height = 5, width = 5)



```



Pollen experiment multi-panel figure
```{r}
(PolExp_1 <- ggarrange(fruit_plot1, vs_plot, nrow = 1, ncol = 2, labels = c("A", "B")))

(PolExp_plot <- ggarrange(PolExp_1, PL_plot_pannel_2, nrow = 2, heights = c(0.4, 0.6)))

ggsave(PolExp_plot, filename = "Figures/PolExp_MainFigure.png", dpi = 300, width = 7, height = 8, units = "in")

```


## Strength of Pollen limitation for fruit set
```{r}
# Fruit Set
PL_fr <- data_all %>%
  mutate(Fruit_PL = Fruit +0.001) %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Open Pollinated") %>% 
  dplyr::select(Population, ID, Treatment, Sex, micro_SR, Fruit_PL) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = Fruit_PL) %>% 
  rename("Open" = "Open Pollinated") %>% 
  # na.omit() %>% 
  mutate(Pollen_Limitation = log(Outcrossed / Open)) 

# Average seed number and calculating raw mean pollen limitation
# Function for standard error
se <- function(x) sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x)))

(PL_fr_output <- PL_fr %>% group_by(Sex) %>% 
  summarise(mean_oc = mean(Outcrossed),
            sd_oc = se(Outcrossed),
            mean_op = mean(Open),
            sd_op = se(Open),
            n = n(),
            pollen_limitation = log(mean(Outcrossed) / mean(Open))))


# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Vectors for Low Hermaphrodite Site
FemOC_fr <- PL_fr %>% filter(Sex == "F") %>% pull(Outcrossed)
FemOP_fr <- PL_fr %>% filter(Sex == "F") %>% pull(Open)
HermOC_fr <- PL_fr %>% filter(Sex == "H") %>% pull(Outcrossed)
HermOP_fr <- PL_fr %>% filter(Sex == "H") %>% pull(Open)

# # Vectors for the high Hermaphrodite group
# High_FemOC_fr <- PL_fr %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
# High_FemOP_fr <- PL_fr %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Open)
# High_HermOC_fr <- PL_fr %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
# High_HermOP_fr <- PL_fr %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Open)

# Create new vectors
Fem_PL_fr <- numeric(0)
Herm_PL_fr <- numeric(0)


nboot <- 1000

for (i in 1:nboot) {
  New_FemOC_fr <- FemOC_fr[sample(1:NROW(FemOC_fr), replace = TRUE)]
  New_FemOP_fr <- FemOP_fr[sample(1:NROW(FemOP_fr), replace = TRUE)]
  New_HermOC_fr <- HermOC_fr[sample(1:NROW(HermOC_fr), replace = TRUE)]
  New_HermOP_fr <- HermOP_fr[sample(1:NROW(HermOP_fr), replace = TRUE)]
  
  Fem_PL_fr[i] <- log(mean(New_FemOC_fr) / mean(New_FemOP_fr))
  Herm_PL_fr[i] <- log(mean(New_HermOC_fr) / mean(New_HermOP_fr))

  
}

hist(Herm_PL_fr)
hist(Fem_PL_fr)



# Estimated mean and confidence interval from bootstrapping
mean(Herm_PL_fr)
quantile(Herm_PL_fr, probs = c(0.025, 0.975))

mean(Fem_PL_fr)
quantile(Fem_PL_fr, probs = c(0.025, 0.975))


# Bias correction because the means are a little different from my estimate using data
expanded_PL_fem <- PL_fr_output %>% 
  filter(Sex == "F") %>% 
  crossing(boots = Fem_PL_fr)

expanded_PL_herm <- PL_fr_output %>% 
  filter(Sex == "H") %>% 
  crossing(boots = Herm_PL_fr)

expanded_PL_fr <- rbind(expanded_PL_fem, expanded_PL_herm)


(PL_fr_bc <- expanded_PL_fr %>% 
  group_by(Sex) %>% 
  summarise(PercLo=quantile(boots,0.025),
            PercHi=quantile(boots,0.975),
            P = length(boots[boots < pollen_limitation])/length(boots),
            Z=qnorm(P,0,1),
            BiasLo=quantile(boots,pnorm(2*Z-1.96)),
            BiasHi=quantile(boots,pnorm(2*Z+1.96))))
  

```



## Strength of Pollen limitation for Cumulative Reproductive Output
```{r}
# Cumulative Reproductive Output
PL_CO <- data_all %>%
  mutate(CO_PL = viable_seed +0.001) %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Open Pollinated") %>% 
  dplyr::select(ID, Treatment, Sex, true_HermCount, CO_PL) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = CO_PL) %>% 
  rename("Open" = "Open Pollinated") %>% 
  na.omit() %>% 
  mutate(Pollen_Limitation = log(Outcrossed / Open))

# Average seed number
(PL_CO_output <- PL_CO %>% group_by(Sex) %>% 
  summarise(mean_oc = mean(Outcrossed),
            se_oc = se(Outcrossed),
            mean_op = mean(Open),
            se_op = se(Open),
            pollen_limitation = log(mean(Outcrossed) / mean(Open))))



# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Vectors for Low Hermaphrodite Site
FemOC_CO <- PL_CO %>% filter(Sex == "F") %>% pull(Outcrossed)
FemOP_CO <- PL_CO %>% filter(Sex == "F") %>% pull(Open)
HermOC_CO <- PL_CO %>% filter(Sex == "H") %>% pull(Outcrossed)
HermOP_CO <- PL_CO %>% filter(Sex == "H") %>% pull(Open)

# Vectors for the high Hermaphrodite group
# High_FemOC_CO <- PL_CO %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
# High_FemOP_CO <- PL_CO %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Open)
# High_HermOC_CO <- PL_CO %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
# High_HermOP_CO <- PL_CO %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Open)

# Create new vectors
Fem_PL_CO <- numeric(0)
Herm_PL_CO <- numeric(0)


nboot <- 1000

for (i in 1:nboot) {
  New_FemOC_CO <- FemOC_CO[sample(1:NROW(FemOC_CO), replace = TRUE)]
  New_FemOP_CO <- FemOP_CO[sample(1:NROW(FemOP_CO), replace = TRUE)]
  New_HermOC_CO <- HermOC_CO[sample(1:NROW(HermOC_CO), replace = TRUE)]
  New_HermOP_CO <- HermOP_CO[sample(1:NROW(HermOP_CO), replace = TRUE)]
  
  Fem_PL_CO[i] <- log(mean(New_FemOC_CO) / mean(New_FemOP_CO))
  Herm_PL_CO[i] <- log(mean(New_HermOC_CO) / mean(New_HermOP_CO))
  
}

hist(Herm_PL_CO)
hist(Fem_PL_CO)




mean(Herm_PL_CO)
quantile(Herm_PL_CO, probs = c(0.025, 0.975))

mean(Fem_PL_CO)
quantile(Fem_PL_CO, probs = c(0.025, 0.975))


# Bias correction because the means are a little different from my estimate using data
expanded_PL_fem_CO <- PL_CO_output %>% 
  filter(Sex == "F") %>% 
  crossing(boots = Fem_PL_CO)

expanded_PL_herm_CO <- PL_CO_output %>% 
  filter(Sex == "H") %>% 
  crossing(boots = Herm_PL_CO)

expanded_PL_CO <- rbind(expanded_PL_fem_CO, expanded_PL_herm_CO)


(PL_CO_bc <- expanded_PL_CO %>% 
  group_by(Sex) %>% 
  summarise(PercLo=quantile(boots,0.025),
            PercHi=quantile(boots,0.975),
            P = length(boots[boots < pollen_limitation])/length(boots),
            Z=qnorm(P,0,1),
            BiasLo=quantile(boots,pnorm(2*Z-1.96)),
            BiasHi=quantile(boots,pnorm(2*Z+1.96))))
  



```


## Strength of Inbreeding Depression for fruit set
```{r}
# Fruit Set
ID_fr <- data_all %>%
  mutate(Fruit_ID = Fruit +0.001) %>% 
  filter(Sex == "H") %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Selfed") %>% 
  dplyr::select(Population, ID, Treatment, micro_SR, Fruit_ID) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = Fruit_ID) %>% 
  na.omit() %>% 
  mutate(Inbreeding_Depression = (Outcrossed - Selfed) / Outcrossed)

# Average seed number and calculating raw mean pollen limitation
(ID_fr_output <- ID_fr %>%  
    ungroup() %>% 
    summarize(mean_oc = mean(Outcrossed),
            se_oc = se(Outcrossed),
            mean_sf = mean(Selfed),
            se_sf = se(Selfed),
            n = n(),
            Inbreeding_Depression = (mean(Outcrossed) - mean(Selfed)) / mean(Outcrossed)))



# Loop to sample data set to get a distribution and confidence intervals for the mean inbreeding depression estimate
# Individual vectors for Low and High Hermaphrodite Site
ID_fr_OC <- ID_fr %>% pull(Outcrossed)
ID_fr_SF <- ID_fr %>% pull(Selfed)

# Create new vectors where average inbreeding depression will be stored
ID_fr_boot <- numeric(0)

# Number of iterations for the bootstrap
nboot <- 1000

for (i in 1:nboot) {
  New_ID_fr_OC <- ID_fr_OC[sample(1:NROW(ID_fr_OC), replace = TRUE)]
  New_ID_fr_SF <- ID_fr_SF[sample(1:NROW(ID_fr_SF), replace = TRUE)]

  ID_fr_boot[i] <- (mean(New_ID_fr_OC) - mean(New_ID_fr_SF)) / mean(New_ID_fr_OC)
}

# Histograms for the iterations of each group
hist(ID_fr_boot)


# Mean and 95% confidence intervals of iterations
mean(ID_fr_boot)
quantile(ID_fr_boot, probs = c(0.025, 0.975))


# Bias correction because the means are a little different from my estimate using data
expanded_ID_fr <- ID_fr_output %>% 
  crossing(boots = ID_fr_boot)


(ID_fr_bc <- expanded_ID_fr %>% 
  summarise(PercLo=quantile(boots,0.025),
            PercHi=quantile(boots,0.975),
            P = length(boots[boots < Inbreeding_Depression])/length(boots),
            Z=qnorm(P,0,1),
            BiasLo=quantile(boots,pnorm(2*Z-1.96)),
            BiasHi=quantile(boots,pnorm(2*Z+1.96))))



```

## Strength of Inbreeding Depression for Cumulative Reproductive Output
```{r}
# Fruit Set
ID_CO <- data_all %>%
  mutate(viable_seed = viable_seed +0.001) %>% 
  filter(Sex == "H") %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Selfed") %>% 
  dplyr::select(Population, ID, Treatment, micro_SR, viable_seed) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = viable_seed) %>% 
  na.omit() %>% 
  mutate(Inbreeding_Depression = (Outcrossed - Selfed) / Outcrossed)

# Average seed number and calculating raw mean pollen limitation
(ID_CO_output <- ID_CO %>% ungroup() %>% 
  summarise(mean_oc = mean(Outcrossed),
            se_oc = se(Outcrossed),
            mean_sf = mean(Selfed),
            se_sf = se(Selfed),
            n = n(),
            Inbreeding_Depression = (mean(Outcrossed) - mean(Selfed)) / mean(Outcrossed)))



# Loop to sample data set to get a distribution and confidence intervals for the mean inbreeding depression estimate
# Individual vectors 
ID_CO_OC <- ID_CO %>% pull(Outcrossed)
ID_CO_SF <- ID_CO %>% pull(Selfed)


# Create new vectors where average inbreeding depression will be stored
ID_CO_boot <- numeric(0)

# Number of iterations for the bootstrap
nboot <- 1000

for (i in 1:nboot) {
  New_ID_CO_OC <- ID_CO_OC[sample(1:NROW(ID_CO_OC), replace = TRUE)]
  New_ID_CO_SF <- ID_CO_SF[sample(1:NROW(ID_CO_SF), replace = TRUE)]

  ID_CO_boot[i] <- (mean(New_ID_CO_OC) - mean(New_ID_CO_SF)) / mean(New_ID_CO_OC)
}

# Histograms for the iterations of each group
hist(ID_CO_boot)


# Mean and 95% confidence intervals of iterations
mean(ID_CO_boot)
quantile(ID_CO_boot, probs = c(0.025, 0.975))

# Bias correction because the means are a little different from my estimate using data
expanded_ID_CO <- ID_CO_output %>% 
  crossing(boots = ID_CO_boot)


(ID_CO_bc <- expanded_ID_CO %>% 
  summarise(PercLo=quantile(boots,0.025),
            PercHi=quantile(boots,0.975),
            P = length(boots[boots < Inbreeding_Depression])/length(boots),
            Z=qnorm(P,0,1),
            BiasLo=quantile(boots,pnorm(2*Z-1.96)),
            BiasHi=quantile(boots,pnorm(2*Z+1.96))))


```


#########################################################################################
## Visualize Data
```{r}
hist(data_seeds$Seed_number)
hist(data_seeds$Germination_rate)

ggplot(data_seeds, aes(x = Treatment, y = Seed_number, fill = Sex)) +
  geom_boxplot() +
  theme_classic()+  
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  facet_wrap(vars(Population))

ggplot(data_seeds, aes(x = Treatment, y = Germination_rate, fill = Sex)) +
  geom_boxplot() +
  theme_classic()+  
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  facet_wrap(vars(Population))

mean_sd <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(germ_mean = mean(Germination_rate), 
            fruit = sum(Fruit),
            n = n(),
            seed_mean = mean(Seed_number),
            germ_sd = sd(Germination_rate),
            seed_se = sd(Seed_number) / (sqrt(n)))

ggplot(data = mean_sd, aes(x = Treatment, y = seed_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = seed_mean - seed_se, ymax = seed_mean + seed_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Mean Number of Viable Seeds") +
  geom_text(
    data = distinct(mean_sd, Population, Treatment, fruit),
    aes(y = -1, label = fruit), position = position_dodge(0.9)) +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population)

```
