---
title: "Pollination Experiment in CO"
author: "Emma"
date: "2024-11-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
remove(list = ls())
set.seed(459813)
# setwd(dir = "Programs/")
```


Load Packages
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggforce) 
library(patchwork)
library(lme4)
library(car)
library(forcats)
library(DHARMa)
library(MuMIn)
library(emmeans)
library(ggpubr)
library(ggeffects)
library(performance)
```


Load data
```{r}
meta <- read.csv("Raw Data/Data/Pollination_Experiment.csv", header = TRUE)
data <- read.csv("Raw Data/Data/Pollination_Experiment_Seeds.csv", header = TRUE)
sex_ratio <- read.csv("Raw Data/Data/Pollen_Deposition.csv")
```

Format sex_ratio dataframe to long format
```{r}
sex_ratio1 <- sex_ratio %>% 
  select(c(Site:Sex, SR_Herm_A, SR_Herm_B, SR_Herm_C, SR_Herm_D)) %>% 
  pivot_longer(cols = starts_with(c("SR_Herm")),
               names_to = c("week"),
               names_prefix = c("SR_Herm_"),
               values_to = c("Herm_Count")) 
  
sex_ratio2 <- sex_ratio %>% 
  select(c(Site:Sex, SR_Fem_A, SR_Fem_B, SR_Fem_C, SR_Fem_D)) %>% 
  pivot_longer(cols = starts_with(c("SR_Fem")),
               names_to = c("week"),
               names_prefix = c("SR_Fem_"),
               values_to = c("Fem_Count")) 

sex_ratio_3 <- merge(sex_ratio1,sex_ratio2, by = c("Site", "Population", "Plot",
                                                     "Plant.ID", "TP", "Sex", "week"), 
                       all.y = TRUE)

sex_ratio_all <- sex_ratio_3 %>% 
  mutate(true_HermCount = if_else(Sex == "H", Herm_Count-1, Herm_Count)) %>% 
  mutate(true_FemCount = if_else(Sex == "F", Fem_Count-1, Fem_Count)) %>% 
  mutate(micro_SR = true_HermCount/(true_FemCount+true_HermCount),
         density = (true_HermCount + true_FemCount + 1) / pi) %>% 
  filter(week == "B") %>% 
  drop_na()


```


Combine dataframes
```{r}
meta2 <- meta %>% mutate(POP_code = ifelse(Population == "East Krummholz", "EK", "WK"))
meta2$ID <- toupper(paste0(meta2$POP_code,meta2$Plant.ID))

data$ID <- toupper(data$ID)
data2<- data %>% 
  mutate(Treatment = case_when(Color == "G" ~ "Outcrossed",
                                              Color == "R" ~ "Selfed",
                                              Color == "B" ~ "No Pollen",
                                              Color == "O" ~ "Open Pollinated"))

data3 <- merge(meta2, data2, by = "ID", all.y = TRUE)

data_all <- merge(data3, sex_ratio_all, by = c("Plant.ID", "Population", "Site", "Plot", "TP", "Sex"))

```


Calculated Variables
```{r}
data_all <- data_all %>% 
  mutate(Germination_rate = data_all$Germinated / data_all$Total_Seeds_end) %>% 
  mutate(Germination_rate = replace_na(Germination_rate, 0))

data_all$viable_seed <- round(data_all$Fruit * data_all$Seed_number * data_all$Germination_rate)

```

Subset dataframe to just include treatments that fruited and remove mix sex. Remove female flower that set fruit in the no pollen treatment.
```{r}
data_all <- data_all %>% 
  filter(Sex != "mix") %>% 
  filter(!(Treatment == "No Pollen" & Sex == "F" & Fruit == 1)) %>% 
  mutate(Fruit_char = case_when(Fruit == 1 ~ "Fruit",
                                Fruit == 0 ~ "No Fruit"),
         Population = case_when(Population == "West Knoll" ~ "Low Hermaphrodite",
                                Population == "East Krummholz" ~ "High Hermaphrodite"))

data_seeds <- data_all %>% 
  filter(Seed_number != 0) %>% 
  drop_na(Population)
```



## Fruit Production
```{r}
data_all$Treatment <- as.factor(data_all$Treatment)
data_all$Sex <- as.factor(data_all$Sex)
  

fruit.m <- glm(Fruit ~ Sex * Treatment+ Sex:(true_FemCount + true_HermCount) + Treatment:(true_FemCount + true_HermCount) + true_FemCount + true_HermCount + Population, data = data_all, family = "binomial")

summary(fruit.m)
Anova(fruit.m)
r.squaredGLMM(fruit.m)

# Check Residuals
qqPlot(resid(fruit.m))

#Check Overdispersion
check_overdispersion(fruit.m)

# Model diagnostics
fruit_res <- simulateResiduals(fruit.m)
plot(fruit_res)


emmeans(fruit.m, specs = pairwise ~ Treatment*Sex, adjust="tukey")


mean_fr <- data_all %>% 
  group_by(Population, Treatment, Sex) %>% 
  summarise(fruit_prop = sum(Fruit) / (n()))

(fruit_plot1 <- ggplot(data = data_all, aes(x = Treatment, fill = fct_rev(Fruit_char))) +
  geom_bar(position = "fill") +
  labs(x = "Pollination Treatment", 
       y = "Fruit Set\n Proportion") +
  theme_classic() +
  scale_fill_manual(values = c("grey", "black")) +
  facet_wrap(~ Sex) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))


# (fruit_micrHermaphrodite <- ggplot(data = Micro_figure, 
#                                    aes(x = x, y = predicted, 
#                                        color = facet, fill = facet)) +
#   geom_line(size = 1) +
#   geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
#   labs(x = "Number of Surrounding Hermaphrodites", y = "Fruit Set\n Proportion") +
#   theme_classic()+
#   scale_fill_manual(values = c("#7A378B", "#66CD00")) +
#   scale_color_manual(values = c("#7A378B", "#66CD00"))+
#   facet_wrap(~group, nrow = 1)+
#   theme(legend.title = element_blank()))


# ggsave(fruit_plot1, filename = "Figures/FruitSet_plot.png", height = 5, width = 5)
```

Inbreeding Depression Figure
```{r}
# Plot effect of micro sex ratio on inbreeding depression
predict1 <- ggpredict(fruit.m, terms = c("true_HermCount [all]", "Treatment", "Sex")) %>% 
  filter(facet == "H" & (group == "Outcrossed" | group == "Selfed"))


predict_ID <- as.data.frame(predict1) %>% 
  select(-facet, -std.error) %>% 
  pivot_wider(names_from = group, 
              values_from = c(predicted, conf.low, conf.high),
              names_sep = ".") %>% 
  mutate(ID = (predicted.Outcrossed-predicted.Selfed)/predicted.Outcrossed)

data_ID <- data_all %>% 
  filter(Sex == "H" & (Treatment == "Outcrossed" | Treatment == "Selfed"))


(ID_plot1 <- ggplot(data = predict1) +
  geom_line(aes(x=x, y=predicted, color = group), size = 1) +
  geom_ribbon(aes(x=x, ymin = conf.low, ymax = conf.high, group = group), alpha = 0.2) +
  geom_jitter(data = data_ID, aes(x = true_HermCount, y = Fruit, color = Treatment), 
              alpha = 0.2, height = 0.05) +
  labs(x = "Hermaphrodite Number", y = "Fruit Set Proportion",
       color = "Treatment") +
  scale_color_manual(values = c("#ADFF2F", "#008B00"))+
  theme_classic()+
  theme(legend.position = "right"))
  
(ID_plot2 <- ggplot() +
  geom_smooth(data = predict_ID, aes(x=x, y=ID), size = 1, se = FALSE, color = "grey50") +
  labs(x = "Hermaphrodite Number", y = "Inbreeding Depression") +
  theme_classic())

(ID_plot <- ggarrange(ID_plot1, ID_plot2, nrow = 1, ncol = 2, labels = c("D", "E"), widths = c(0.60,0.40)))

ggsave(ID_plot, file = "./Figures/ID_plot.png", width = 8, height = 4, units = "in", dpi = 300)
```

Pollen Limitation figure
```{r}
# Plot of pollen limitation
predict2 <- ggpredict(fruit.m, terms = c("true_HermCount [all]", "Treatment", "Sex")) %>%
  filter(group == "Outcrossed" | group == "Open Pollinated")  


predict_PL <- as.data.frame(predict2) %>% 
  select(-std.error) %>% 
  pivot_wider(names_from = group, 
              values_from = c(predicted, conf.low, conf.high),
              names_sep = ".") %>% 
  rename(predicted.Open = 'predicted.Open Pollinated',
         conf.low.Open = 'conf.low.Open Pollinated',
         conf.high.Open = 'conf.high.Open Pollinated') %>% 
  mutate(PL = log(predicted.Outcrossed/predicted.Open))

predict_F <- predict2 %>% 
  filter(facet == "F") 

predict_H <- predict2 %>% 
  filter(facet == "H")

data_PL_F <- data_all %>% 
  filter(Sex == "F" & (Treatment == "Outcrossed" | Treatment == "Open Pollinated"))
data_PL_H <- data_all %>% 
  filter(Sex == "H" & (Treatment == "Outcrossed" | Treatment == "Open Pollinated"))

(PL_F_plot <- ggplot() +
  geom_line(data = predict_F, aes(x=x, y=predicted, color = group), size = 1) +
  geom_ribbon(data = predict_F, 
              aes(x=x, ymin = conf.low, ymax = conf.high, group = group), alpha = 0.2) +
  geom_jitter(data = data_PL_F, aes(x = true_HermCount, y = Fruit, color = Treatment), 
              alpha = 0.6, height = 0.05) +
  labs(x = "", y = "Fruit Set Proportion", 
       title ="Female", color = "") +
  scale_color_manual(values = c("#68228B", "#E066FF")) +
  theme_classic() +
  theme(legend.position = "top"))

(PL_H_plot <- ggplot() +
  geom_line(data = predict_H, aes(x=x, y=predicted, color = group), size = 1) +
  geom_ribbon(data = predict_H, 
              aes(x=x, ymin = conf.low, ymax = conf.high, group = group), alpha = 0.2) +
  geom_jitter(data = data_PL_H, aes(x = true_HermCount, y = Fruit, color = Treatment), 
              alpha = 0.4, height = 0.05) +
  labs(x = "", 
       y = "Fruit Set Proportion",
       title = "Hermaphrodite", color = "") +
  scale_color_manual(values = c("#008B00", "#ADFF2F"))+
  theme_classic()+
  theme(legend.position = "top"))



(PL_plot <- ggplot() +
  geom_smooth(data = predict_PL, aes(x=x, y=PL, color = facet), size = 1, se = FALSE) +
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  labs(x = "", y = "Pollen Limitation",
       color = "Sex") +
  theme_classic() +
  theme(legend.position = "top"))

(PL_plot_pannel <- ggarrange(PL_F_plot, PL_H_plot, PL_plot, ncol = 3, widths = c(0.3,0.3,0.4), labels = c("A", "B","C")))

(PL_ID_PANNEL <- ggarrange(PL_plot_pannel, ID_plot, nrow = 2))

ggsave(ID_plot, file = "./Figures/PL_ID_Panel.png", width = 8, height = 6, units = "in", dpi = 300)

```


## Seed Production
```{r}
seeds.m <- glm(Seed_number ~ Sex * Treatment + Sex:(true_FemCount + true_HermCount) + Treatment:(true_FemCount + true_HermCount) + true_FemCount + true_HermCount + Population, data = data_seeds, family = "poisson")

summary(seeds.m)
Anova(seeds.m)
r.squaredGLMM(seeds.m)


mean_sd <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(seed_mean = mean(Seed_number),
            n = n(),
            seed_se = sd(Seed_number) / (sqrt(n)))

(seed_plot <- ggplot(data = mean_sd, aes(x = Treatment, y = seed_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = seed_mean - seed_se, ymax = seed_mean + seed_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Seed Number") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population, ncol = 2) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position="top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

ggsave(seed_plot, filename = "Figures/Seed_Supp.png", dpi = 300, width = 6, height = 4, units = "in")

(seed_plot2 <- ggplot(data = data_all, aes(x = true_HermCount, y = Seed_number, color = Sex)) +
  geom_point(position = "dodge", alpha = 0.5) +
  geom_smooth(method = "glm", se = T, 
        method.args = list(family = "poisson")) +
  labs(x = "Micro Hermaphrodite Count", y = "Seed Count")+
  theme_classic()+
  facet_wrap(vars(Treatment)) +
  scale_color_manual(values = c("#7A378B", "#66CD00")))

```


## Seed Germination
```{r}

germ.m <- glm(cbind(Germinated, (Total_Seeds_end - Germinated)) ~ Sex * Treatment + Sex:(true_FemCount + true_HermCount) + Treatment:(true_FemCount + true_HermCount) + true_FemCount + true_HermCount + Population, data = data_seeds, family = "binomial")

summary(germ.m)
Anova(germ.m)
r.squaredGLMM(germ.m)


mean_germ <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(germ_mean = mean(Germination_rate),
            n = n(),
            germ_se = sd(Germination_rate) / (sqrt(n)))

(germ_plot <- ggplot(data = mean_germ, aes(x = Treatment, y = germ_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = germ_mean - germ_se, ymax = germ_mean + germ_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Germination Rate") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population, ncol = 2) +
  theme(legend.title = element_blank(),
        legend.position="none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

ggsave(germ_plot, filename = "Figures/Germ_Supp.png", dpi = 300, width = 6, height = 4, units = "in")

# Average germination rate for each treatment
data_seeds %>% group_by(Treatment) %>% 
  summarise(Mean_GermRate = mean(Germination_rate),
            SD_GermRate = sd(Germination_rate),
            Mean_Seed = mean(Seed_number),
            SD_Seed = sd(Seed_number))

```


## Cummulative reproductive output
```{r}

viable_seeds.m <- MASS::glm.nb(viable_seed ~ Sex * Treatment + true_HermCount + true_FemCount + Sex:true_HermCount + Treatment:true_HermCount + Population, data = data_all)

summary(viable_seeds.m)
Anova(viable_seeds.m)
r.squaredGLMM(viable_seeds.m)



fig_germ <- data_all %>% 
  replace(is.na(.), 0) %>% 
  mutate(Figure_vs = Fruit * Seed_number * Germination_rate) %>% 
  drop_na(Figure_vs) %>% 
  group_by(Sex, Treatment) %>% 
  summarise(viable_mean = mean(Figure_vs),
            n = n(),
            viable_se = sd(Figure_vs) / (sqrt(n)))


(vs_plot <- ggplot(data = fig_germ, aes(x = Treatment, y = viable_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = viable_mean - viable_se, ymax = viable_mean + viable_se), 
                position = position_dodge(0.9), width = 0.25) +
  # geom_hline(yintercept = 1.25, linetype = "dotted") +
  labs(x = "Pollination Treatment", y = "Cumulative \nReproductive Output") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~Sex) +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

ggsave(vs_plot, filename = "Figures/cumulative_plot.png", height = 5, width = 5)


alpha <- c(1,1,1,1,0.2,1,1,1,1,1,1,1,0.2,1)

(vs_plot_zoom <- ggplot(data = fig_germ, aes(x = Treatment, y = viable_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge(), alpha = alpha) +
  geom_errorbar(aes(ymin = viable_mean - viable_se, ymax = viable_mean + viable_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  coord_cartesian(ylim = c(0,1.2)) +
  theme(legend.title = element_blank(),
        legend.position="none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))



```



Pollen experiment multi-panel figure
```{r}
(PolExp_plot <- ggarrange(fruit_plot1, fruit_micrHermaphrodite, vs_plot, nrow = 3, ncol = 1, labels = c("A", "B", "C")))

ggsave(filename = "Figures/PolExp_MainFigure.png", dpi = 300, width = 6, height = 7.5, units = "in")

```


## Strength of Pollen limitation for fruit set
```{r}
# Fruit Set
PL_fr <- data_all %>%
  mutate(Fruit_PL = Fruit +0.001) %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Open Pollinated") %>% 
  select(Population, ID, Treatment, Sex, micro_SR, Fruit_PL) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = Fruit_PL) %>% 
  rename("Open" = "Open Pollinated") %>% 
  na.omit() %>% 
  mutate(Pollen_Limitation = log(Outcrossed / Open))

# Average seed number and calculating raw mean pollen limitation
PL_fr %>% group_by(Sex, Population) %>% 
  summarise(mean_oc = mean(Outcrossed),
            sd_oc = sd(Outcrossed),
            mean_op = mean(Open),
            sd_op = sd(Open),
            pollen_limitation = log(mean(Outcrossed) / mean(Open)))


ggplot(PL_fr, aes(x = micro_SR, y = Pollen_Limitation, colour = Sex)) +
  geom_jitter(width = 0.3, height = 0.025, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(c("binomial"))) +
  labs(x = "Micro Sex Ratio", y = "Pollen Limitation")+
  theme_classic()+
  facet_wrap(vars(Population))+
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "none")

# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Vectors for Low Hermaphrodite Site
Low_FemOC_fr <- PL_fr %>% filter(Sex == "F" & Population == "Low Hermaphrodite") %>% pull(Outcrossed)
Low_FemOP_fr <- PL_fr %>% filter(Sex == "F" & Population == "Low Hermaphrodite") %>% pull(Open)
Low_HermOC_fr <- PL_fr %>% filter(Sex == "H" & Population == "Low Hermaphrodite") %>% pull(Outcrossed)
Low_HermOP_fr <- PL_fr %>% filter(Sex == "H" & Population == "Low Hermaphrodite") %>% pull(Open)

# Vectors for the high Hermaphrodite group
High_FemOC_fr <- PL_fr %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
High_FemOP_fr <- PL_fr %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Open)
High_HermOC_fr <- PL_fr %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
High_HermOP_fr <- PL_fr %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Open)

# Create new vectors
High_Fem_PL_fr <- numeric(0)
High_Herm_PL_fr <- numeric(0)
Low_Fem_PL_fr <- numeric(0)
Low_Herm_PL_fr <- numeric(0)

nboot <- 1000

for (i in 1:nboot) {
  New_Low_FemOC_fr <- Low_FemOC_fr[sample(1:NROW(Low_FemOC_fr), replace = TRUE)]
  New_Low_FemOP_fr <- Low_FemOP_fr[sample(1:NROW(Low_FemOP_fr), replace = TRUE)]
  New_Low_HermOC_fr <- Low_HermOC_fr[sample(1:NROW(Low_HermOC_fr), replace = TRUE)]
  New_Low_HermOP_fr <- Low_HermOP_fr[sample(1:NROW(Low_HermOP_fr), replace = TRUE)]
  New_High_FemOC_fr <- High_FemOC_fr[sample(1:NROW(High_FemOC_fr), replace = TRUE)]
  New_High_FemOP_fr <- High_FemOP_fr[sample(1:NROW(High_FemOP_fr), replace = TRUE)]
  New_High_HermOC_fr <- High_HermOC_fr[sample(1:NROW(High_HermOC_fr), replace = TRUE)]
  New_High_HermOP_fr <- High_HermOP_fr[sample(1:NROW(High_HermOP_fr), replace = TRUE)]
  
  High_Fem_PL_fr[i] <- log(mean(New_High_FemOC_fr) / mean(New_High_FemOP_fr))
  High_Herm_PL_fr[i] <- log(mean(New_High_HermOC_fr) / mean(New_High_HermOP_fr))
  Low_Fem_PL_fr[i] <- log(mean(New_Low_FemOC_fr) / mean(New_Low_FemOP_fr))
  Low_Herm_PL_fr[i] <- log(mean(New_Low_HermOC_fr) / mean(New_Low_HermOP_fr))
  
}

hist(Low_Herm_PL_fr)
hist(Low_Fem_PL_fr)
hist(High_Herm_PL_fr)
hist(Low_Fem_PL_fr)



mean(Low_Herm_PL_fr)
quantile(Low_Herm_PL_fr, probs = c(0.025, 0.975))

mean(Low_Fem_PL_fr)
quantile(Low_Fem_PL_fr, probs = c(0.025, 0.975))

mean(High_Herm_PL_fr)
quantile(High_Herm_PL_fr, probs = c(0.025, 0.975))

mean(High_Fem_PL_fr)
quantile(High_Fem_PL_fr, probs = c(0.025, 0.975))

```



## Strength of Pollen limitation for seed set
```{r}
# Seed Number
PL_sn <- data_all %>%
  mutate(Seed_PL = Seed_number +0.001) %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Open Pollinated") %>% 
  select(Population, ID, Treatment, Sex, micro_SR, Seed_PL) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = Seed_PL) %>% 
  rename("Open" = "Open Pollinated") %>% 
  na.omit() %>% 
  mutate(Pollen_Limitation = log(Outcrossed / Open))

# Average seed number
PL_sn %>% group_by(Population, Sex) %>% 
  summarise(mean_oc = mean(Outcrossed),
            sd_oc = sd(Outcrossed),
            mean_op = mean(Open),
            sd_op = sd(Open),
            pollen_limitation = log(mean(Outcrossed) / mean(Open)))


ggplot(PL_sn, aes(x = micro_SR, y = Pollen_Limitation, colour = Sex)) +
  geom_jitter(width = 0.3, height = 0.025, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(c("binomial"))) +
  labs(x = "Micro Sex Ratio", y = "Pollen Limitation")+
  theme_classic()+
  facet_wrap(vars(Population))+
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "none")


# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Vectors for Low Hermaphrodite Site
Low_FemOC_sn <- PL_sn %>% filter(Sex == "F" & Population == "Low Hermaphrodite") %>% pull(Outcrossed)
Low_FemOP_sn <- PL_sn %>% filter(Sex == "F" & Population == "Low Hermaphrodite") %>% pull(Open)
Low_HermOC_sn <- PL_sn %>% filter(Sex == "H" & Population == "Low Hermaphrodite") %>% pull(Outcrossed)
Low_HermOP_sn <- PL_sn %>% filter(Sex == "H" & Population == "Low Hermaphrodite") %>% pull(Open)

# Vectors for the high Hermaphrodite group
High_FemOC_sn <- PL_sn %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
High_FemOP_sn <- PL_sn %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Open)
High_HermOC_sn <- PL_sn %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
High_HermOP_sn <- PL_sn %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Open)

# Create new vectors
High_Fem_PL_sn <- numeric(0)
High_Herm_PL_sn <- numeric(0)
Low_Fem_PL_sn <- numeric(0)
Low_Herm_PL_sn <- numeric(0)

nboot <- 1000

for (i in 1:nboot) {
  New_Low_FemOC_sn <- Low_FemOC_sn[sample(1:NROW(Low_FemOC_sn), replace = TRUE)]
  New_Low_FemOP_sn <- Low_FemOP_sn[sample(1:NROW(Low_FemOP_sn), replace = TRUE)]
  New_Low_HermOC_sn <- Low_HermOC_sn[sample(1:NROW(Low_HermOC_sn), replace = TRUE)]
  New_Low_HermOP_sn <- Low_HermOP_sn[sample(1:NROW(Low_HermOP_sn), replace = TRUE)]
  New_High_FemOC_sn <- High_FemOC_sn[sample(1:NROW(High_FemOC_sn), replace = TRUE)]
  New_High_FemOP_sn <- High_FemOP_sn[sample(1:NROW(High_FemOP_sn), replace = TRUE)]
  New_High_HermOC_sn <- High_HermOC_sn[sample(1:NROW(High_HermOC_sn), replace = TRUE)]
  New_High_HermOP_sn <- High_HermOP_sn[sample(1:NROW(High_HermOP_sn), replace = TRUE)]
  
  High_Fem_PL_sn[i] <- log(mean(New_High_FemOC_sn) / mean(New_High_FemOP_sn))
  High_Herm_PL_sn[i] <- log(mean(New_High_HermOC_sn) / mean(New_High_HermOP_sn))
  Low_Fem_PL_sn[i] <- log(mean(New_Low_FemOC_sn) / mean(New_Low_FemOP_sn))
  Low_Herm_PL_sn[i] <- log(mean(New_Low_HermOC_sn) / mean(New_Low_HermOP_sn))
  
}

hist(Low_Herm_PL)
hist(Low_Fem_PL)
hist(High_Herm_PL)
hist(Low_Fem_PL)



mean(Low_Herm_PL_sn)
quantile(Low_Herm_PL_sn, probs = c(0.025, 0.975))

mean(Low_Fem_PL_sn)
quantile(Low_Fem_PL_sn, probs = c(0.025, 0.975))

mean(High_Herm_PL_sn)
quantile(High_Herm_PL_sn, probs = c(0.025, 0.975))

mean(High_Fem_PL_sn)
quantile(High_Fem_PL_sn, probs = c(0.025, 0.975))


```


## Strength of Pollen limitation for Cumulative Reproductive Output
```{r}
# Cumulative Reproductive Output
PL_CO <- data_all %>%
  mutate(CO_PL = viable_seed +0.001) %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Open Pollinated") %>% 
  select(Population, ID, Treatment, Sex, true_HermCount, CO_PL) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = CO_PL) %>% 
  rename("Open" = "Open Pollinated") %>% 
  na.omit() %>% 
  mutate(Pollen_Limitation = log(Outcrossed / Open))

# Average seed number
PL_CO %>% group_by(Population, Sex) %>% 
  summarise(mean_oc = mean(Outcrossed),
            sd_oc = sd(Outcrossed),
            mean_op = mean(Open),
            sd_op = sd(Open),
            pollen_limitation = log(mean(Outcrossed) / mean(Open)))



# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Vectors for Low Hermaphrodite Site
Low_FemOC_CO <- PL_CO %>% filter(Sex == "F" & Population == "Low Hermaphrodite") %>% pull(Outcrossed)
Low_FemOP_CO <- PL_CO %>% filter(Sex == "F" & Population == "Low Hermaphrodite") %>% pull(Open)
Low_HermOC_CO <- PL_CO %>% filter(Sex == "H" & Population == "Low Hermaphrodite") %>% pull(Outcrossed)
Low_HermOP_CO <- PL_CO %>% filter(Sex == "H" & Population == "Low Hermaphrodite") %>% pull(Open)

# Vectors for the high Hermaphrodite group
High_FemOC_CO <- PL_CO %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
High_FemOP_CO <- PL_CO %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Open)
High_HermOC_CO <- PL_CO %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
High_HermOP_CO <- PL_CO %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Open)

# Create new vectors
High_Fem_PL_CO <- numeric(0)
High_Herm_PL_CO <- numeric(0)
Low_Fem_PL_CO <- numeric(0)
Low_Herm_PL_CO <- numeric(0)

nboot <- 1000

for (i in 1:nboot) {
  New_Low_FemOC_CO <- Low_FemOC_CO[sample(1:NROW(Low_FemOC_CO), replace = TRUE)]
  New_Low_FemOP_CO <- Low_FemOP_CO[sample(1:NROW(Low_FemOP_CO), replace = TRUE)]
  New_Low_HermOC_CO <- Low_HermOC_CO[sample(1:NROW(Low_HermOC_CO), replace = TRUE)]
  New_Low_HermOP_CO <- Low_HermOP_CO[sample(1:NROW(Low_HermOP_CO), replace = TRUE)]
  New_High_FemOC_CO <- High_FemOC_CO[sample(1:NROW(High_FemOC_CO), replace = TRUE)]
  New_High_FemOP_CO <- High_FemOP_CO[sample(1:NROW(High_FemOP_CO), replace = TRUE)]
  New_High_HermOC_CO <- High_HermOC_CO[sample(1:NROW(High_HermOC_CO), replace = TRUE)]
  New_High_HermOP_CO <- High_HermOP_CO[sample(1:NROW(High_HermOP_CO), replace = TRUE)]
  
  High_Fem_PL_CO[i] <- log(mean(New_High_FemOC_CO) / mean(New_High_FemOP_CO))
  High_Herm_PL_CO[i] <- log(mean(New_High_HermOC_CO) / mean(New_High_HermOP_CO))
  Low_Fem_PL_CO[i] <- log(mean(New_Low_FemOC_CO) / mean(New_Low_FemOP_CO))
  Low_Herm_PL_CO[i] <- log(mean(New_Low_HermOC_CO) / mean(New_Low_HermOP_CO))
  
}

hist(Low_Herm_PL)
hist(Low_Fem_PL)
hist(High_Herm_PL)
hist(Low_Fem_PL)



mean(Low_Herm_PL_CO)
quantile(Low_Herm_PL_CO, probs = c(0.025, 0.975))

mean(Low_Fem_PL_CO)
quantile(Low_Fem_PL_CO, probs = c(0.025, 0.975))

mean(High_Herm_PL_CO)
quantile(High_Herm_PL_CO, probs = c(0.025, 0.975))

mean(High_Fem_PL_CO)
quantile(High_Fem_PL_CO, probs = c(0.025, 0.975))


```


## Strength of Inbreeding Depression for fruit set
```{r}
# Fruit Set
ID_fr <- data_all %>%
  mutate(Fruit_ID = Fruit +0.001) %>% 
  filter(Sex == "H") %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Selfed") %>% 
  select(Population, ID, Treatment, micro_SR, Fruit_ID) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = Fruit_ID) %>% 
  na.omit() %>% 
  mutate(Inbreeding_Depression = (Outcrossed - Selfed) / Outcrossed)

# Average seed number and calculating raw mean pollen limitation
ID_fr %>% group_by(Population)  %>% 
  summarise(mean_oc = mean(Outcrossed),
            sd_oc = sd(Outcrossed),
            mean_sf = mean(Selfed),
            sd_sf = sd(Selfed),
            Inbreeding_Depression = (mean(Outcrossed) - mean(Selfed)) / mean(Outcrossed))


ggplot(ID_fr, aes(x = micro_SR, y = Inbreeding_Depression)) +
  geom_jitter(width = 0.3, height = 0.025, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(c("binomial"))) +
  labs(x = "Micro Sex Ratio", y = "Inbreedng Depression")+
  theme_classic()+
  facet_wrap(vars(Population))+
  scale_color_manual("#66CD00")+
  theme(legend.position = "none")

# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Individual vectors for Low Hermaphrodite Site
FemOC <- PL_fr %>% filter(Sex == "F") %>% pull(Outcrossed)
FemOP <- PL_fr %>% filter(Sex == "F") %>% pull(Open)
HermOC <- PL_fr %>% filter(Sex == "H") %>%  pull(Outcrossed)
HermOP <- PL_fr %>% filter(Sex == "H") %>% pull(Open)

# Individual vectors for the high Hermaphrodite group
# High_FemOC <- PL_fr %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
# High_FemOP <- PL_fr %>% filter(Sex == "F" & Population == "High Hermaphrodite") %>% pull(Open)
# High_HermOC <- PL_fr %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Outcrossed)
# High_HermOP <- PL_fr %>% filter(Sex == "H" & Population == "High Hermaphrodite") %>% pull(Open)

# Create new vectors where average pollen limitation will be stored
Fem_PL <- numeric(0)
Herm_PL <- numeric(0)


# Number of iterations for the bootstrap
nboot <- 1000

for (i in 1:nboot) {
  New_FemOC <- FemOC[sample(1:NROW(FemOC), replace = TRUE)]
  New_FemOP <- FemOP[sample(1:NROW(FemOP), replace = TRUE)]
  New_HermOC <- HermOC[sample(1:NROW(HermOC), replace = TRUE)]
  New_HermOP <- HermOP[sample(1:NROW(HermOP), replace = TRUE)]
  # New_High_FemOC <- High_FemOC[sample(1:NROW(High_FemOC), replace = TRUE)]
  # New_High_FemOP <- High_FemOP[sample(1:NROW(High_FemOP), replace = TRUE)]
  # New_High_HermOC <- High_HermOC[sample(1:NROW(High_HermOC), replace = TRUE)]
  # New_High_HermOP <- High_HermOP[sample(1:NROW(High_HermOP), replace = TRUE)]
  
  Fem_PL[i] <- log(mean(New_FemOC) / mean(New_FemOP))
  Herm_PL[i] <- log(mean(New_HermOC) / mean(New_HermOP))
  # Low_Fem_PL[i] <- log(mean(New_Low_FemOC) / mean(New_Low_FemOP))
  # Low_Herm_PL[i] <- log(mean(New_Low_HermOC) / mean(New_Low_HermOP))
  
}

# Histograms for the iterations of each group
hist(Herm_PL)
hist(Fem_PL)



# Mean and 95% confidence intervals of iterations
mean(Herm_PL)
quantile(Herm_PL, probs = c(0.025, 0.975))

mean(Fem_PL)
quantile(Fem_PL, probs = c(0.025, 0.975))

# mean(High_Herm_PL)
# quantile(High_Herm_PL, probs = c(0.025, 0.975))
# 
# mean(High_Fem_PL)
# quantile(High_Fem_PL, probs = c(0.025, 0.975))



```




#########################################################################################
## Visualize Data
```{r}
hist(data_seeds$Seed_number)
hist(data_seeds$Germination_rate)

ggplot(data_seeds, aes(x = Treatment, y = Seed_number, fill = Sex)) +
  geom_boxplot() +
  theme_classic()+  
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  facet_wrap(vars(Population))

ggplot(data_seeds, aes(x = Treatment, y = Germination_rate, fill = Sex)) +
  geom_boxplot() +
  theme_classic()+  
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  facet_wrap(vars(Population))

mean_sd <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(germ_mean = mean(Germination_rate), 
            fruit = sum(Fruit),
            n = n(),
            seed_mean = mean(Seed_number),
            germ_sd = sd(Germination_rate),
            seed_se = sd(Seed_number) / (sqrt(n)))

ggplot(data = mean_sd, aes(x = Treatment, y = seed_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = seed_mean - seed_se, ymax = seed_mean + seed_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Mean Number of Viable Seeds") +
  geom_text(
    data = distinct(mean_sd, Population, Treatment, fruit),
    aes(y = -1, label = fruit), position = position_dodge(0.9)) +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population)

```
