---
title: "Pollination Experiment in CO"
author: "Emma"
date: "2024-11-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
remove(list = ls())
set.seed(459813)
```


Load Packages
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggforce) 
library(patchwork)
library(lme4)
library(car)
library(forcats)
library(MuMIn)
library(emmeans)
library(ggpubr)
```


Load data
```{r}
meta <- read.csv("Raw Data/Data/Pollination_Experiment.csv", header = TRUE)
data <- read.csv("Raw Data/Data/Pollination_Experiment_Seeds.csv", header = TRUE)
sex_ratio <- read.csv("Raw Data/Data/Pollen_Deposition.csv")
```

Format sex_ratio dataframe to long format
```{r}
sex_ratio1 <- sex_ratio %>% 
  select(c(Site:Sex, SR_Herm_A, SR_Herm_B, SR_Herm_C, SR_Herm_D)) %>% 
  pivot_longer(cols = starts_with(c("SR_Herm")),
               names_to = c("week"),
               names_prefix = c("SR_Herm_"),
               values_to = c("Herm_Count")) 
  
sex_ratio2 <- sex_ratio %>% 
  select(c(Site:Sex, SR_Fem_A, SR_Fem_B, SR_Fem_C, SR_Fem_D)) %>% 
  pivot_longer(cols = starts_with(c("SR_Fem")),
               names_to = c("week"),
               names_prefix = c("SR_Fem_"),
               values_to = c("Fem_Count")) 

sex_ratio_3 <- merge(sex_ratio1,sex_ratio2, by = c("Site", "Population", "Plot",
                                                     "Plant.ID", "TP", "Sex", "week"), 
                       all.y = TRUE)

sex_ratio_all <- sex_ratio_3 %>% 
  mutate(true_HermCount = if_else(Sex == "H", Herm_Count-1, Herm_Count)) %>% 
  mutate(true_FemCount = if_else(Sex == "F", Fem_Count-1, Fem_Count)) %>% 
  mutate(micro_SR = true_HermCount/(true_FemCount+true_HermCount),
         density = (true_HermCount + true_FemCount + 1) / pi) %>% 
  filter(week == "B") %>% 
  drop_na()


```


Combine dataframes
```{r}
meta2 <- meta %>% mutate(POP_code = ifelse(Population == "East Krummholz", "EK", "WK"))
meta2$ID <- toupper(paste0(meta2$POP_code,meta2$Plant.ID))

data$ID <- toupper(data$ID)
data2<- data %>% 
  mutate(Treatment = case_when(Color == "G" ~ "Outcrossed",
                                              Color == "R" ~ "Selfed",
                                              Color == "B" ~ "No Pollen",
                                              Color == "O" ~ "Open Pollinated"))

data3 <- merge(meta2, data2, by = "ID", all.y = TRUE)

data_all <- merge(data3, sex_ratio_all, by = c("Plant.ID", "Population", "Site", "Plot", "TP", "Sex"))

```


Calculated Variables
```{r}
data_all <- data_all %>% 
  mutate(Germination_rate = data_all$Germinated / data_all$Total_Seeds_end) %>% 
  mutate(Germination_rate = replace_na(Germination_rate, 0))

data_all$viable_seed <- round(data_all$Fruit * data_all$Seed_number * data_all$Germination_rate)

```

Subset dataframe to just include treatments that fruited and remove mix sex
```{r}
data_all <- data_all %>% filter(Sex != "mix") %>% 
  mutate(Fruit_char = case_when(Fruit == 1 ~ "Fruit",
                                Fruit == 0 ~ "No Fruit"),
         Population = case_when(Population == "West Knoll" ~ "Low OSR",
                                Population == "East Krummholz" ~ "High OSR"))

data_seeds <- data_all %>% 
  filter(Seed_number != 0) %>% 
  drop_na(Population)
```



## Fruit Production
```{r}
fruit.m <- glm(Fruit ~ Sex * Treatment * (true_HermCount + Population), data = data_all, family = "binomial")

summary(fruit.m)
Anova(fruit.m)
r.squaredGLMM(fruit.m)

pairs(emmeans(fruit.m, specs = pairwise ~ Treatment|Sex|Population, adjust="tukey"), reverse = TRUE)


mean_fr <- data_all %>% 
  group_by(Population, Treatment, Sex) %>% 
  summarise(fruit_prop = sum(Fruit) / (n()))

(fruit_plot1 <- ggplot(data = data_all, aes(x = Treatment, fill = fct_rev(Fruit_char))) +
  geom_bar(position = "fill") +
  labs(x = "Pollination Treatment", 
       y = "Fruit Set Proportion") +
  theme_classic() +
  scale_fill_manual(values = c("grey", "black")) +
  facet_grid(Sex ~ Population, drop = TRUE, 
             labeller = as_labeller(c('Low OSR' = "Low OSR",'High OSR' = "High OSR",
                                      'F' = "Female", 'H' = "Hermaphrodite"))) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "top", 
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))



(fruit_plot2 <- ggplot(data = data_all, aes(x = true_HermCount, y = Fruit, color = Treatment)) +
  geom_jitter(width = 0, height = 0.025, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(c("binomial"))) +
  labs(x = "Micro Sex Ratio", y = "Fruit Production")+
  theme_classic()+
  facet_wrap(vars(Sex)) +
  scale_color_manual(values = c("#1E90FF", "#104E8B", "#00CD00", "#EEC900")))



(fruit_plot2 <- ggplot(data = data_all, aes(x = true_HermCount, y = Fruit, color = Sex)) +
  geom_jitter(width = 0, height = 0.025, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(c("binomial"))) +
  labs(x = "Micro Herm", y = "Fruit Production")+
  theme_classic()+
  facet_wrap(vars(Treatment)) +
  scale_color_manual(values = c("#7A378B", "#66CD00")))


data_all %>% 
  group_by(Sex, Population) %>% 
  summarize(n = n())

data_all %>% 
  group_by(Sex, Population) %>% 
  filter(Fruit == 1) %>% 
  summarize(n = n())

meta %>% 
  group_by(Sex, Population) %>% 
  summarize(n = n())

```


## Seed Production
```{r}
seeds.m <- glm(Seed_number ~ Sex * Treatment * (true_HermCount +Population), data = data_seeds, family = "poisson")

summary(seeds.m)
Anova(seeds.m)
r.squaredGLMM(seeds.m)

pairs(emmeans(seeds.m, specs = pairwise ~ Treatment|Sex|Population, adjust="tukey"), reverse = TRUE)


mean_sd <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(seed_mean = mean(Seed_number),
            n = n(),
            seed_se = sd(Seed_number) / (sqrt(n)))

(seed_plot <- ggplot(data = mean_sd, aes(x = Treatment, y = seed_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = seed_mean - seed_se, ymax = seed_mean + seed_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Seed Number") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population, ncol = 2) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        legend.position="top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))

(seed_plot2 <- ggplot(data = data_all, aes(x = true_HermCount, y = Seed_number, color = Sex)) +
  geom_point(position = "dodge", alpha = 0.5) +
  geom_smooth(method = "glm", se = T, 
        method.args = list(family = "poisson")) +
  labs(x = "Micro Hermaphrodite Count", y = "Seed Count")+
  theme_classic()+
  facet_wrap(vars(Treatment)) +
  scale_color_manual(values = c("#7A378B", "#66CD00")))

```


## Seed Germination
```{r}

germ.m <- glm(cbind(Germinated, (Total_Seeds_end - Germinated)) ~ Sex * Treatment * Population, data = data_seeds, family = "binomial")

summary(germ.m)
Anova(germ.m)
r.squaredGLMM(germ.m)


pairs(emmeans(germ.m, specs = pairwise ~ Treatment|Sex|Population, adjust="tukey"), reverse = TRUE)


mean_germ <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(germ_mean = mean(Germination_rate),
            n = n(),
            germ_se = sd(Germination_rate) / (sqrt(n)))

(germ_plot <- ggplot(data = mean_germ, aes(x = Treatment, y = germ_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = germ_mean - germ_se, ymax = germ_mean + germ_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Germination Rate") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population, ncol = 2) +
  theme(legend.title = element_blank(),
        legend.position="none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))




```


## Cummulative reproductive output
```{r}

viable_seeds.m <- glm(viable_seed ~ Sex * Treatment * (Population + true_HermCount), data = data_all, family = "poisson")

summary(viable_seeds.m)
Anova(viable_seeds.m)
r.squaredGLMM(viable_seeds.m)


pairs(emmeans(viable_seeds.m, specs = pairwise ~ Treatment|Sex|Population, adjust="tukey"), reverse = TRUE)


fig_germ <- data_all %>% 
  replace(is.na(.), 0) %>% 
  mutate(Figure_vs = Fruit * Seed_number * Germination_rate) %>% 
  drop_na(Figure_vs) %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(viable_mean = mean(Figure_vs),
            n = n(),
            viable_se = sd(Figure_vs) / (sqrt(n)))



(vs_plot <- ggplot(data = fig_germ, aes(x = Treatment, y = viable_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = viable_mean - viable_se, ymax = viable_mean + viable_se), 
                position = position_dodge(0.9), width = 0.25) +
  geom_hline(yintercept = 1.25, linetype = "dotted") +
  labs(x = "Pollination Treatment", y = "Cumulative \nReproductive Output") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population, ncol = 2) +
  theme(legend.title = element_blank(),
        legend.position="none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))


alpha <- c(1,1,1,1,0.2,1,1,1,1,1,1,1,0.2,1)

(vs_plot_zoom <- ggplot(data = fig_germ, aes(x = Treatment, y = viable_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge(), alpha = alpha) +
  geom_errorbar(aes(ymin = viable_mean - viable_se, ymax = viable_mean + viable_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population, ncol = 2) +
  coord_cartesian(ylim = c(0,1.2)) +
  theme(legend.title = element_blank(),
        legend.position="none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))



```



Pollen experiment multi-panel figure
```{r}
ggarrange(fruit_plot, seed_plot, vs_plot, vs_plot_zoom, nrow = 2, ncol = 2, labels = c("A", "B", "C", "D"))
```


## Strength of Pollen limitation for fruit set
```{r}
# Fruit Set
PL_fr <- data_all %>%
  mutate(Fruit_PL = Fruit +0.001) %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Open Pollinated") %>% 
  select(Population, ID, Treatment, Sex, micro_SR, Fruit_PL) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = Fruit_PL) %>% 
  rename("Open" = "Open Pollinated") %>% 
  na.omit() %>% 
  mutate(Pollen_Limitation = log(Outcrossed / Open))

# Average seed number and calculating raw mean pollen limitation
PL_fr %>% group_by(Population, Sex) %>% 
  summarise(mean_oc = mean(Outcrossed),
            sd_oc = sd(Outcrossed),
            mean_op = mean(Open),
            sd_op = sd(Open),
            pollen_limitation = log(mean(Outcrossed) / mean(Open)))


ggplot(PL_fr, aes(x = micro_SR, y = Pollen_Limitation, colour = Sex)) +
  geom_jitter(width = 0.3, height = 0.025, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(c("binomial"))) +
  labs(x = "Micro Sex Ratio", y = "Pollen Limitation")+
  theme_classic()+
  facet_wrap(vars(Population))+
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "none")

# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Individual vectors for Low OSR Site
Low_FemOC <- PL_fr %>% filter(Sex == "F" & Population == "Low OSR") %>% pull(Outcrossed)
Low_FemOP <- PL_fr %>% filter(Sex == "F" & Population == "Low OSR") %>% pull(Open)
Low_HermOC <- PL_fr %>% filter(Sex == "H" & Population == "Low OSR") %>%  pull(Outcrossed)
Low_HermOP <- PL_fr %>% filter(Sex == "H" & Population == "Low OSR") %>% pull(Open)

# Individual vectors for the high OSR group
High_FemOC <- PL_fr %>% filter(Sex == "F" & Population == "High OSR") %>% pull(Outcrossed)
High_FemOP <- PL_fr %>% filter(Sex == "F" & Population == "High OSR") %>% pull(Open)
High_HermOC <- PL_fr %>% filter(Sex == "H" & Population == "High OSR") %>% pull(Outcrossed)
High_HermOP <- PL_fr %>% filter(Sex == "H" & Population == "High OSR") %>% pull(Open)

# Create new vectors where average pollen limitation will be stored
High_Fem_PL <- numeric(0)
High_Herm_PL <- numeric(0)
Low_Fem_PL <- numeric(0)
Low_Herm_PL <- numeric(0)

# Number of iterations for the bootstrap
nboot <- 1000

for (i in 1:nboot) {
  New_Low_FemOC <- Low_FemOC[sample(1:NROW(Low_FemOC), replace = TRUE)]
  New_Low_FemOP <- Low_FemOP[sample(1:NROW(Low_FemOP), replace = TRUE)]
  New_Low_HermOC <- Low_HermOC[sample(1:NROW(Low_HermOC), replace = TRUE)]
  New_Low_HermOP <- Low_HermOP[sample(1:NROW(Low_HermOP), replace = TRUE)]
  New_High_FemOC <- High_FemOC[sample(1:NROW(High_FemOC), replace = TRUE)]
  New_High_FemOP <- High_FemOP[sample(1:NROW(High_FemOP), replace = TRUE)]
  New_High_HermOC <- High_HermOC[sample(1:NROW(High_HermOC), replace = TRUE)]
  New_High_HermOP <- High_HermOP[sample(1:NROW(High_HermOP), replace = TRUE)]
  
  High_Fem_PL[i] <- log(mean(New_High_FemOC) / mean(New_High_FemOP))
  High_Herm_PL[i] <- log(mean(New_High_HermOC) / mean(New_High_HermOP))
  Low_Fem_PL[i] <- log(mean(New_Low_FemOC) / mean(New_Low_FemOP))
  Low_Herm_PL[i] <- log(mean(New_Low_HermOC) / mean(New_Low_HermOP))
  
}

# Histograms for the iterations of each group
hist(Low_Herm_PL)
hist(Low_Fem_PL)
hist(High_Herm_PL)
hist(Low_Fem_PL)


# Mean and 95% confidence intervals of iterations
mean(Low_Herm_PL)
quantile(Low_Herm_PL, probs = c(0.025, 0.975))

mean(Low_Fem_PL)
quantile(Low_Fem_PL, probs = c(0.025, 0.975))

mean(High_Herm_PL)
quantile(High_Herm_PL, probs = c(0.025, 0.975))

mean(High_Fem_PL)
quantile(High_Fem_PL, probs = c(0.025, 0.975))



```



## Strength of Pollen limitation for seed set
```{r}
# Seed Number
PL_sn <- data_all %>%
  mutate(Seed_PL = Seed_number +0.001) %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Open Pollinated") %>% 
  select(Population, ID, Treatment, Sex, micro_SR, Seed_PL) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = Seed_PL) %>% 
  rename("Open" = "Open Pollinated") %>% 
  na.omit() %>% 
  mutate(Pollen_Limitation = log(Outcrossed / Open))

# Average seed number
PL_sn %>% group_by(Population, Sex) %>% 
  summarise(mean_oc = mean(Outcrossed),
            sd_oc = sd(Outcrossed),
            mean_op = mean(Open),
            sd_op = sd(Open),
            pollen_limitation = log(mean(Outcrossed) / mean(Open)))


ggplot(PL_sn, aes(x = micro_SR, y = Pollen_Limitation, colour = Sex)) +
  geom_jitter(width = 0.3, height = 0.025, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(c("binomial"))) +
  labs(x = "Micro Sex Ratio", y = "Pollen Limitation")+
  theme_classic()+
  facet_wrap(vars(Population))+
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "none")


# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Vectors for Low OSR Site
Low_FemOC_sn <- PL_sn %>% filter(Sex == "F" & Population == "Low OSR") %>% pull(Outcrossed)
Low_FemOP_sn <- PL_sn %>% filter(Sex == "F" & Population == "Low OSR") %>% pull(Open)
Low_HermOC_sn <- PL_sn %>% filter(Sex == "H" & Population == "Low OSR") %>% pull(Outcrossed)
Low_HermOP_sn <- PL_sn %>% filter(Sex == "H" & Population == "Low OSR") %>% pull(Open)

# Vectors for the high OSR group
High_FemOC_sn <- PL_sn %>% filter(Sex == "F" & Population == "High OSR") %>% pull(Outcrossed)
High_FemOP_sn <- PL_sn %>% filter(Sex == "F" & Population == "High OSR") %>% pull(Open)
High_HermOC_sn <- PL_sn %>% filter(Sex == "H" & Population == "High OSR") %>% pull(Outcrossed)
High_HermOP_sn <- PL_sn %>% filter(Sex == "H" & Population == "High OSR") %>% pull(Open)

# Create new vectors
High_Fem_PL_sn <- numeric(0)
High_Herm_PL_sn <- numeric(0)
Low_Fem_PL_sn <- numeric(0)
Low_Herm_PL_sn <- numeric(0)

nboot <- 1000

for (i in 1:nboot) {
  New_Low_FemOC_sn <- Low_FemOC_sn[sample(1:NROW(Low_FemOC_sn), replace = TRUE)]
  New_Low_FemOP_sn <- Low_FemOP_sn[sample(1:NROW(Low_FemOP_sn), replace = TRUE)]
  New_Low_HermOC_sn <- Low_HermOC_sn[sample(1:NROW(Low_HermOC_sn), replace = TRUE)]
  New_Low_HermOP_sn <- Low_HermOP_sn[sample(1:NROW(Low_HermOP_sn), replace = TRUE)]
  New_High_FemOC_sn <- High_FemOC_sn[sample(1:NROW(High_FemOC_sn), replace = TRUE)]
  New_High_FemOP_sn <- High_FemOP_sn[sample(1:NROW(High_FemOP_sn), replace = TRUE)]
  New_High_HermOC_sn <- High_HermOC_sn[sample(1:NROW(High_HermOC_sn), replace = TRUE)]
  New_High_HermOP_sn <- High_HermOP_sn[sample(1:NROW(High_HermOP_sn), replace = TRUE)]
  
  High_Fem_PL_sn[i] <- log(mean(New_High_FemOC_sn) / mean(New_High_FemOP_sn))
  High_Herm_PL_sn[i] <- log(mean(New_High_HermOC_sn) / mean(New_High_HermOP_sn))
  Low_Fem_PL_sn[i] <- log(mean(New_Low_FemOC_sn) / mean(New_Low_FemOP_sn))
  Low_Herm_PL_sn[i] <- log(mean(New_Low_HermOC_sn) / mean(New_Low_HermOP_sn))
  
}

hist(Low_Herm_PL)
hist(Low_Fem_PL)
hist(High_Herm_PL)
hist(Low_Fem_PL)



mean(Low_Herm_PL_sn)
quantile(Low_Herm_PL_sn, probs = c(0.025, 0.975))

mean(Low_Fem_PL_sn)
quantile(Low_Fem_PL_sn, probs = c(0.025, 0.975))

mean(High_Herm_PL_sn)
quantile(High_Herm_PL_sn, probs = c(0.025, 0.975))

mean(High_Fem_PL_sn)
quantile(High_Fem_PL_sn, probs = c(0.025, 0.975))


```


## Strength of Pollen limitation for Cumulative Reproductive Output
```{r}
# Cumulative Reproductive Output
PL_CO <- data_all %>%
  mutate(CO_PL = viable_seed +0.001) %>% 
  filter(Treatment == "Outcrossed" | Treatment == "Open Pollinated") %>% 
  select(Population, ID, Treatment, Sex, true_HermCount, CO_PL) %>% 
  group_by(ID) %>% 
  pivot_wider(names_from = Treatment, values_from = CO_PL) %>% 
  rename("Open" = "Open Pollinated") %>% 
  na.omit() %>% 
  mutate(Pollen_Limitation = log(Outcrossed / Open))

# Average seed number
PL_CO %>% group_by(Population, Sex) %>% 
  summarise(mean_oc = mean(Outcrossed),
            sd_oc = sd(Outcrossed),
            mean_op = mean(Open),
            sd_op = sd(Open),
            pollen_limitation = log(mean(Outcrossed) / mean(Open)))



# Loop to sample data set to get a distribution and confidence intervals for the mean pollen limitation estimate
# Vectors for Low OSR Site
Low_FemOC_CO <- PL_CO %>% filter(Sex == "F" & Population == "Low OSR") %>% pull(Outcrossed)
Low_FemOP_CO <- PL_CO %>% filter(Sex == "F" & Population == "Low OSR") %>% pull(Open)
Low_HermOC_CO <- PL_CO %>% filter(Sex == "H" & Population == "Low OSR") %>% pull(Outcrossed)
Low_HermOP_CO <- PL_CO %>% filter(Sex == "H" & Population == "Low OSR") %>% pull(Open)

# Vectors for the high OSR group
High_FemOC_CO <- PL_CO %>% filter(Sex == "F" & Population == "High OSR") %>% pull(Outcrossed)
High_FemOP_CO <- PL_CO %>% filter(Sex == "F" & Population == "High OSR") %>% pull(Open)
High_HermOC_CO <- PL_CO %>% filter(Sex == "H" & Population == "High OSR") %>% pull(Outcrossed)
High_HermOP_CO <- PL_CO %>% filter(Sex == "H" & Population == "High OSR") %>% pull(Open)

# Create new vectors
High_Fem_PL_CO <- numeric(0)
High_Herm_PL_CO <- numeric(0)
Low_Fem_PL_CO <- numeric(0)
Low_Herm_PL_CO <- numeric(0)

nboot <- 1000

for (i in 1:nboot) {
  New_Low_FemOC_CO <- Low_FemOC_CO[sample(1:NROW(Low_FemOC_CO), replace = TRUE)]
  New_Low_FemOP_CO <- Low_FemOP_CO[sample(1:NROW(Low_FemOP_CO), replace = TRUE)]
  New_Low_HermOC_CO <- Low_HermOC_CO[sample(1:NROW(Low_HermOC_CO), replace = TRUE)]
  New_Low_HermOP_CO <- Low_HermOP_CO[sample(1:NROW(Low_HermOP_CO), replace = TRUE)]
  New_High_FemOC_CO <- High_FemOC_CO[sample(1:NROW(High_FemOC_CO), replace = TRUE)]
  New_High_FemOP_CO <- High_FemOP_CO[sample(1:NROW(High_FemOP_CO), replace = TRUE)]
  New_High_HermOC_CO <- High_HermOC_CO[sample(1:NROW(High_HermOC_CO), replace = TRUE)]
  New_High_HermOP_CO <- High_HermOP_CO[sample(1:NROW(High_HermOP_CO), replace = TRUE)]
  
  High_Fem_PL_CO[i] <- log(mean(New_High_FemOC_CO) / mean(New_High_FemOP_CO))
  High_Herm_PL_CO[i] <- log(mean(New_High_HermOC_CO) / mean(New_High_HermOP_CO))
  Low_Fem_PL_CO[i] <- log(mean(New_Low_FemOC_CO) / mean(New_Low_FemOP_CO))
  Low_Herm_PL_CO[i] <- log(mean(New_Low_HermOC_CO) / mean(New_Low_HermOP_CO))
  
}

hist(Low_Herm_PL)
hist(Low_Fem_PL)
hist(High_Herm_PL)
hist(Low_Fem_PL)



mean(Low_Herm_PL_CO)
quantile(Low_Herm_PL_CO, probs = c(0.025, 0.975))

mean(Low_Fem_PL_CO)
quantile(Low_Fem_PL_CO, probs = c(0.025, 0.975))

mean(High_Herm_PL_CO)
quantile(High_Herm_PL_CO, probs = c(0.025, 0.975))

mean(High_Fem_PL_CO)
quantile(High_Fem_PL_CO, probs = c(0.025, 0.975))


```




#########################################################################################
## Visualize Data
```{r}
hist(data_seeds$Seed_number)
hist(data_seeds$Germination_rate)

ggplot(data_seeds, aes(x = Treatment, y = Seed_number, fill = Sex)) +
  geom_boxplot() +
  theme_classic()+  
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  facet_wrap(vars(Population))

ggplot(data_seeds, aes(x = Treatment, y = Germination_rate, fill = Sex)) +
  geom_boxplot() +
  theme_classic()+  
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  facet_wrap(vars(Population))

mean_sd <- data_seeds %>% 
  group_by(Sex, Treatment, Population) %>% 
  summarise(germ_mean = mean(Germination_rate), 
            fruit = sum(Fruit),
            n = n(),
            seed_mean = mean(Seed_number),
            germ_sd = sd(Germination_rate),
            seed_se = sd(Seed_number) / (sqrt(n)))

ggplot(data = mean_sd, aes(x = Treatment, y = seed_mean, fill = Sex)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = seed_mean - seed_se, ymax = seed_mean + seed_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Pollination Treatment", y = "Mean Number of Viable Seeds") +
  geom_text(
    data = distinct(mean_sd, Population, Treatment, fruit),
    aes(y = -1, label = fruit), position = position_dodge(0.9)) +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  facet_wrap(~ Population)

```
