---
title: "Pollen Deposition in CO"
author: "Emma"
date: "2025-01-14"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
remove(list = ls())
```


Load Packages
```{r, warning=FALSE, message=FALSE}
library(MASS)
library(tidyverse)
library(lme4)
library(lmerTest)
library(MuMIn)
library(ggpubr)
library(car)
library(rsq)
library(MuMIn)
library(boot)
library(emmeans)
library(merTools)
library(DHARMa)
library(ggpubr)
library(ggeffects)
library(scales)
library(performance)
library(plotrix)
library(prevalence)
library(cowplot)
```


Load data
```{r}
meta <- read.csv("Raw_Data/Data/Pollen_Deposition.csv", header = TRUE)
data <- read.csv("Raw_Data/Data/Pollen_Deposition_Data_all.csv", header = TRUE)

data_2025 <- read.csv("Raw_Data/Data/Ovule_Count_2025.csv")
meta_2025 <- read.csv("Raw_Data/Data/Ovule_Count_2025_meta.csv", header = TRUE)

sex_dat <- read.csv("Raw_Data/Data/Sex_Ratio_2023.csv")
```


Format sex ratio data
```{r}
sex_ratio1 <- meta %>% 
  dplyr::select(Site:Sex, SR_Herm_A, SR_Herm_B, SR_Herm_C, SR_Herm_D) %>% 
  pivot_longer(cols = starts_with(c("SR_Herm")),
               names_to = c("Week"),
               names_prefix = c("SR_Herm_"),
               values_to = c("Herm_Count")) 
  
sex_ratio2 <- meta %>% 
  dplyr::select(c(Site:Sex, SR_Fem_A, SR_Fem_B, SR_Fem_C, SR_Fem_D)) %>% 
  pivot_longer(cols = starts_with(c("SR_Fem")),
               names_to = c("Week"),
               names_prefix = c("SR_Fem_"),
               values_to = c("Fem_Count")) 

sex_ratio_all <- merge(sex_ratio1,sex_ratio2, 
                       by = c("Site", "Population", "Plot","Plant.ID", "TP", "Sex", "Week"), 
                       all.y = TRUE)

sex_ratio_all <- sex_ratio_all %>% 
  mutate(true_HermCount = if_else(Sex == "H", Herm_Count-1, Herm_Count)) %>% 
  mutate(true_FemCount = if_else(Sex == "F", Fem_Count-1, Fem_Count)) %>% 
  mutate(micro_SR = true_HermCount/(true_FemCount+true_HermCount),
         density = (true_HermCount + true_FemCount + 1) / pi)



```

Format stigma data
```{r}

meta <- meta %>% mutate_if(is.numeric, as.character)
  

stigma1 <- meta %>% 
  dplyr::select(c(Site:Sex, starts_with("Stig"))) %>% 
  pivot_longer(cols = starts_with(c("Stig")),
               names_to = c("Week_Flower"),
               names_prefix = c("Stig_"),
               values_to = c("Tube_Number")) %>% 
  separate_wider_position(Week_Flower, c(Week = 1, Flower = 1))

notes <- meta %>% 
  dplyr::select(c(Plant.ID, ends_with("_Notes"))) %>% 
  pivot_longer(cols = ends_with(c("_Notes")),
               names_to = c("Week_Flower"),
               values_to = c("Field_Notes"),
               names_pattern = "(.*)_Notes") %>% 
  separate_wider_position(Week_Flower, c(Week = 1, Flower = 1))

stigma2 <- merge(stigma1, notes, by = c("Plant.ID", "Week", "Flower"), all.x = TRUE)





```


Combine dataframes
```{r}
stigma3 <- merge(stigma2, data, by = "Tube_Number", all.y = TRUE)


stigma4 <- merge(stigma3, sex_ratio_all, 
                 by = c("Site", "Population", "Plot", "Plant.ID", "TP", "Sex", "Week"), 
                 all.x = TRUE)

# Remove individuals with female and hermaphrodite mix 
stigma5 <- stigma4 %>% filter(Sex != "mix")
```


Turn individual flower herbivory notes, pollen deposition, and female function into binomial data
```{r}
stigma6 <- stigma5 %>% 
  mutate(herb = if_else(Field_Notes == "herb", 1, 0)) %>% 
  mutate(Herbivory = if_else(herb == "0" | is.na(herb), "No Florivory", "Florivory")) %>% 
  mutate(pollen_depo = if_else(Pollen_Number_1 == 0, 0, 1)) %>% 
  mutate(female_func = if_else(Ovule_Number_1 == 0, 0, 1)) %>% 
  mutate(Population = case_when(Population == "West Knoll" ~ "Low Hermaphrodite",
                                Population == "East Krummholz" ~ "High Hermaphrodite"))


write.csv(stigma6, "Output/micro_SR_formatted.csv", row.names = FALSE)

```


Site level sex ratios 
```{r}
# Site level sex ratio from micro sex ratio each time flowers were marked for stigma collection
stigma6 %>% 
  group_by(Population, Week) %>% 
  summarise(sex_ratio = sum(true_HermCount) / sum(true_HermCount + true_FemCount))

# Site level sex ratio from micro sex ratio - all observations
MeanMicro_SR <- stigma6 %>% 
  group_by(Plant.ID, Population) %>% 
  summarise(mean_SR = mean(true_HermCount/ (true_HermCount + true_FemCount))) %>% 
  group_by(Population) %>% 
  na.omit() %>% 
  summarise(sex_ratio = mean(mean_SR))

# Graph showing the distribution of micro sex ratio
(na_counts <- stigma6 %>%
  filter(is.na(micro_SR)) %>%
  group_by(Sex, Population) %>%
  summarise(na_count = n(), .groups = "drop") %>%
  mutate(micro_SR = 1.1)) # Use Inf to place NA bars outside the histogram range

stigma6 %>% group_by(Plant.ID, Population, Sex) %>%  
  summarise(mean_SR = mean(true_HermCount/ (true_HermCount + true_FemCount))) %>% 
  ggplot(aes(x = mean_SR, fill = Sex)) +
  geom_vline(data = MeanMicro_SR, aes(xintercept=sex_ratio), 
             linetype="dashed", size = 1) +
  geom_histogram(position = "dodge", na.rm = FALSE, binwidth = 0.05) +
  geom_col(data = na_counts, aes(x = micro_SR, y = na_count, fill = Sex), 
           position = "dodge", width = 0.05, inherit.aes = FALSE, 
           alpha = 0.5) +
  labs(x = "Micro Sex Ratio", y = "Count") +
  theme_classic() +
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  facet_wrap(~ Population, ncol = 1) +
  annotate("text", x = 1.1, y = -2, label = "NA")



# Site level sex ratio from surveys and confidence intervals
sex_dat %>% 
  filter(Smut != "Y" &
         Population == "West Knoll" | Population == "East Krummholz") %>% 
  group_by(Population) %>% 
  summarise(n = length(Sex), x = sum(str_count(Sex, "H")))

propCI(x = 85, 200, method = "all", level = 0.95, sortby = "level") #West Knoll
propCI(x = 149, n = 200, method = "all", level = 0.95, sortby = "level") #East Krummholz
  

# Total observations
stigma6 %>% 
  drop_na(Stigma_Length) %>% 
  group_by(Sex, Population) %>% 
  summarise(n = n_distinct(Plant.ID))

meta %>% 
  group_by(Sex, Population) %>% 
  summarise(n = n_distinct(Plant.ID))
```


## How does herbivory differ between the two sexes?
```{r}
herbivory.m <- glmer(herb ~ Sex * Population + (1|Plant.ID), data = stigma6, family = "binomial") 

summary(herbivory.m)
Anova(herbivory.m)

emmeans(herbivory.m, specs = pairwise ~ Sex|Population, adjust="tukey", type = "response")


ggplot(stigma6, aes(x = Herbivory, fill = Sex)) +
  geom_bar() +
  theme_classic()+
  facet_wrap(vars(Population))+
  labs(y = "Count") +
  scale_fill_manual(values = c("#7A378B", "#66CD00"))

ggsave("Figures/Florivory.png", width = 6, height = 4, units = "in")

```


Remove observations with herbivory on the stigma or ovary
```{r}
# Remove observations with herbivory of stigmas
stigma_all <- stigma6 %>% filter(Stigma_Herbivory != 1 | Ovule_Herbivory != 1)
```



### Format ovule data from 2025 and merge with ovule data from 2024
```{r}

data_all_2025 <- merge(meta_2025, data_2025, by = c("Plant.ID", "Sex"))

# Drop observations with stigmas that have a length affected by herbivory and create a variable based on if there is female function or not
data_all_2025_2 <- data_all_2025 %>% 
  filter(Stigma_Herbivory != 1,
         Seeds != 1,
         Duplicates != 1) %>% 
  mutate(female_func = if_else(Ovule_Number_1 == 0, 0, 1),
         Site = "Niwot")

Ovule_data <- bind_rows(stigma_all, data_all_2025_2)

```




## How do floral traits differ between sexes and individuals?
### Stigma Length
```{r}
# Stigma length
q1_stig.m <- lmer(Stigma_Length ~ Sex + (Sex|Population) + (1|Plant.ID), data = Ovule_data)

summary(q1_stig.m)
r.squaredGLMM(q1_stig.m)
Anova(q1_stig.m)
ranova(q1_stig.m)

# Check Residuals
qqPlot(resid(q1_stig.m))

#Check Overdispersion
check_overdispersion(q1_stig.m)

stig_res <- simulateResiduals(q1_stig.m)
plot(stig_res)

# Get difference between stigma lengths for females and hermaphrodites
emmeans(q1_stig.m, "Sex")


# stigma length plot with model estimates
predict <- ggpredict(q1_stig.m, terms = c("Sex"))

(stig_plot <- ggplot() +
    geom_violin(data = Ovule_data, 
                aes(x = Sex, y = Stigma_Length, fill = Sex), 
                alpha = 0.25, color = NA) +
    geom_errorbar(data = predict, aes(x = x, ymin = conf.low, ymax = conf.high, color = x), 
                  width = 0.1, size = 0.2) +
    geom_point(data = predict, 
               aes(x = x, y = predicted, color = x), 
               size = 2) +
    ylab("Stigma Length (mm)") +
    xlab("") +
    theme_classic() +  
    scale_fill_manual(values = c("#7A378B", "#66CD00")) +
    scale_color_manual(values = c("#491561", "#366E02")) +
    theme(legend.position = "none"))
    

# Stigma length violin plot
ggplot(Ovule_data, aes(x = Sex, y = Stigma_Length, fill = Sex)) +
  geom_violin(alpha = 0.25) +
  geom_boxplot(width = 0.2) +
  ylab("Stigma Length (mm)") +
  theme_classic()+  
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  # facet_wrap(~ Population) +
  theme(legend.position = "none")



```


## Female Function
### Hurdle Modle for Ovule Development

Binomial Model - likelihood of producing or aborting ovules
```{r}

q1_ovule_binom.m <- glmer(female_func ~ Sex * Stigma_Length + (Sex|Population) + (1|Plant.ID), data = Ovule_data, family = "binomial")

# Different optimizer
q1_ovule_binom.m2 <- update(q1_ovule_binom.m, control = glmerControl(optimizer = "bobyqa"))

summary(q1_ovule_binom.m2)
r.squaredGLMM(q1_ovule_binom.m2)
Anova(q1_ovule_binom.m2)

# Test fixed effect of site by sex
RE_ovule_binom.m1 <- glmer(female_func ~ Sex * Stigma_Length +(1|Plant.ID), data = Ovule_data, family = "binomial")
anova(q1_ovule_binom.m, RE_ovule_binom.m1)
# Test fixed effect of plant ID
RE_ovule_binom.m2 <- glmer(female_func ~ Sex * Stigma_Length +(Sex|Population), data = Ovule_data, family = "binomial")
anova(q1_ovule_binom.m, RE_ovule_binom.m2)

emmeans(q1_ovule_binom.m, specs = pairwise ~ Sex, type = "response")


# Check Residuals
qqPlot(resid(q1_ovule_binom.m))

#Check Overdispersion
check_overdispersion(q1_ovule_binom.m)

# Model diagnostics
ovbin_res <- simulateResiduals(q1_ovule_binom.m)
plot(ovbin_res)

# Make plot
predict <- ggpredict(q1_ovule_binom.m, terms = c("Stigma_Length", "Sex"))

(ov_plot1 <- ggplot(data = predict, aes(x=x, y=predicted, color = group)) +  
  geom_smooth(size = 1, se = FALSE, aes(color = group)) +
  geom_ribbon(data = predict, aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2) +
  geom_jitter(data=Ovule_data, aes(x = Stigma_Length, y = female_func, color = Sex), 
              height = 0.1) +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  scale_color_manual(values = c("#7A378B", "#66CD00")) +
  theme_classic()+  
  ylab("Mean Female Function \n(Proportion of Flowers with Ovules)") +
  xlab("Stigma Length (mm)")+
  theme(legend.position = "none"))



# Are there functional males?
(ov_plot2 <- Ovule_data %>% 
  dplyr::select(Population, Sex, Plant.ID, female_func) %>% 
  mutate(Sex = if_else(Sex == "F", "Female", "Hermaphrodite")) %>% 
  na.omit(female_func) %>% 
    group_by(Sex, Plant.ID) %>%  
  mutate(mean_female_func = mean(female_func, na.rm = TRUE),
         Number = n()) %>%
  ungroup() %>%
  mutate(Plant.ID = factor(Plant.ID, levels = 
                             unique(Plant.ID[order(mean_female_func)]))) %>%
  ggerrorplot(x="Plant.ID", y="female_func",
              color="Sex", palette=c("#7A378B", "#66CD00"),
              desc_stat = "mean_se",
              position = position_dodge(0.3),
              size = 0.05,
              xlab="Individual Plants", 
              ylab="Mean Female Function \n(Proportion of Flowers with Ovules)",
              facet.by = "Sex") +
  geom_point(aes(x=Plant.ID, y=mean_female_func, 
                 size = Number, color = Sex), alpha = 0.1) +
  labs(size = "Flower Number") +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        legend.position = "right"))


stigma_all %>% 
  drop_na(female_func) %>% 
  group_by(Sex, Population, Plant.ID) %>% 
  mutate(mean_female_func = mean(female_func, na.rm = TRUE)) %>% 
  filter(mean_female_func == 0) %>% 
  summarise(n = n()) %>% 
  ungroup(Population, Sex) %>% 
  summarise (mean_n = mean(n),
             range_n = range(n))



```

### Ovule Number
```{r}
# Ovule Number
ovule1 <- Ovule_data %>% filter(female_func == 1)

q1_ovule_num.m <- glmer.nb(Ovule_Number_1 ~ Sex * Stigma_Length + (Sex|Population) + (1|Plant.ID), data = ovule1, verbose = TRUE)

summary(q1_ovule_num.m)
Anova(q1_ovule_num.m)
r.squaredGLMM(q1_ovule_num.m)


RE_ovule_num.m <- glmer.nb(Ovule_Number_1 ~ Sex * Stigma_Length + (1|Population), 
                               data = ovule1)
anova(q1_ovule_num.m, RE_ovule_num.m)


# Check Residuals
qqPlot(resid(q1_ovule_num.m))

#Check Overdispersion
check_overdispersion(q1_ovule_num.m)

# Model diagnostics
ovnum_res <- simulateResiduals(q1_ovule_num.m)
plot(ovnum_res)


# Make plot
predict <- ggpredict(q1_ovule_num.m, terms = c("Stigma_Length"))

ggplot(data = predict, aes(x=x, y=predicted), color = "black") +  
  geom_smooth(size = 1, se = FALSE, color = "black") +
  geom_ribbon(data = predict, aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_jitter(data=ovule1, aes(x = Stigma_Length, y = Ovule_Number_1), 
              height = 0.1, color = "black") +
  theme_classic()+  
  ylab("Ovule Number") +
  xlab("Stigma Length (mm)")+
  theme(legend.position = "none")


ggplot(ovule1, aes(x = Sex, y = Ovule_Number_1, fill = Sex)) +
  geom_violin(alpha = 0.25) +
  geom_boxplot(width = 0.15) +
  theme_classic()+  
  ylab("Ovule Number") +
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "none")


# Make inlay plots for ovule figure
predict <- ggpredict(q1_ovule_num.m, terms = c("Sex")) %>% 
  filter(x == "F")

(Ovule_violin_F <- Ovule_data %>% filter(Sex == "F") %>% 
  ggplot() +
    geom_violin(aes(x = Sex, y = Ovule_Number_1, fill = Sex), 
                alpha = 0.25, color = NA) +
    geom_errorbar(data = predict, aes(x = x, ymin = conf.low, ymax = conf.high, color = x), 
                  width = 0.1, size = 0.2) +
    geom_point(data = predict, 
               aes(x = x, y = predicted, color = x), 
               size = 2) +
    ylab("Ovule Number") +
    xlab("") +
    theme_classic() +  
    scale_fill_manual(values = "#7A378B") +
    scale_color_manual(values = "#491561") +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks = element_blank()))

ggsave("Figures/Ovule_violin_F.png", width = 1, height = 2.5, units = "in")

predict <- ggpredict(q1_ovule_num.m, terms = c("Sex")) %>% 
  filter(x == "H")

(Ovule_violin_H <-Ovule_data %>% filter(Sex == "H") %>% 
  ggplot() +
    geom_violin(aes(x = Sex, y = Ovule_Number_1, fill = Sex), 
                alpha = 0.25, color = NA) +
    geom_errorbar(data = predict, aes(x = x, ymin = conf.low, ymax = conf.high, color = x), 
                  width = 0.1, size = 0.2) +
    geom_point(data = predict, 
               aes(x = x, y = predicted, color = x), 
               size = 2) +
    ylab("Ovule Number") +
    xlab("") +
    theme_classic() +  
    scale_fill_manual(values = "#66CD00") +
    scale_color_manual(values = "#366E02") +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks = element_blank()))


ggsave("Figures/Ovule_violin_H.png", width = 1, height = 2.5, units = "in")

```

Floral Trait multipanel figure
```{r}
(FloralTrait_Panel <- ggarrange(ggarrange(stig_plot, ov_plot1, ncol = 2, nrow = 1, labels = c("A", "B")), ov_plot2, nrow = 2, labels = c("", "C"), heights = c(1, 1.5)))

ggsave("Figures/FloralTrait_Panel.png", width = 8, height = 7, units = "in", bg = "white", dpi = 300)
```



## How do floral traits, sex, and micro sex ratio impact pollination?
### Hurdle Model for Pollen Deposition

Pollen Deposition Binomial
```{r}
q2_pollen_depo_SL.m <- glmer(pollen_depo ~ (Stigma_Length + true_HermCount) * Sex + true_FemCount + Population + (1|Plant.ID), data = stigma_all, family = "binomial")

# Different optimizer
q2_pollen_depo_SL.m2 <- update(q2_pollen_depo_SL.m, control = glmerControl(optimizer = "bobyqa"))

summary(q2_pollen_depo_SL.m2)
r.squaredGLMM(q2_pollen_depo_SL.m2)
Anova(q2_pollen_depo_SL.m2)

RE_pollen_depo_SL.m <- glm(pollen_depo ~ (Stigma_Length + true_HermCount) * Sex + Population, data = stigma_all, family = "binomial")

anova(q2_pollen_depo_SL.m, RE_pollen_depo_SL.m)


# Check Residuals
qqPlot(resid(q2_pollen_depo_SL.m))

#Check Overdispersion
check_overdispersion(q2_pollen_depo_SL.m)

# Model diagnostics
polbin_res <- simulateResiduals(q2_pollen_depo_SL.m)
plot(polbin_res)


emmeans(q2_pollen_depo_SL.m, specs = pairwise ~ Sex|Population, type = "response")
emmeans(q2_pollen_depo_SL.m, specs = pairwise ~ Sex|Stigma_Length, type = "response")


# Make Plot for stigma length
pollen_bin <- stigma_all %>% 
  mutate(Sex = if_else(Sex == "F", "Female", "Hermaphrodite"))

predict <- ggpredict(q2_pollen_depo_SL.m, terms = c("Stigma_Length", "Sex"))%>% 
  as.data.frame() %>% 
  mutate(Sex = case_when(group == "F" ~ "Female",
                         group == "H" ~ "Hermaphrodite"))

(pollen_stig_plot1 <- ggplot(data = predict, aes(x=x, y=predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, group = Sex), alpha = 0.2) +
  geom_smooth(size = 1, se = FALSE, aes(color=Sex)) +
  geom_jitter(data=pollen_bin, aes(x = Stigma_Length, y = pollen_depo, 
                              group = Sex, color = Sex), width = 0.3, 
                              height = 0.025, alpha = 0.5) +
  labs(x = "Stigma Length (mm)", y = "Probability of\n Pollen Deposition", color = "Sex")+
  theme_classic()+
  scale_color_manual(values = c("#7A378B", "#66CD00")) +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  theme(legend.position = "none"))

ggsave(pollen_stig_plot1, file = "./Figures/Pollen_Depo1.png", dpi = 300, width = 6, height = 5)



# Make Plot for hermaphrodite number and sex interaction

predict2 <- ggpredict(q2_pollen_depo_SL.m, terms = c("true_HermCount", "Sex")) %>% 
  as.data.frame() %>% 
  mutate(Sex = case_when(group == "F" ~ "Female",
                         group == "H" ~ "Hermaphrodite"))

(pollen_SR_plot <- ggplot(data = predict2, aes(x=x, y=predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, group = Sex), alpha = 0.2) +
  geom_smooth(size = 1, se = FALSE, aes(color=Sex)) +
  geom_jitter(data=pollen_bin, aes(x = true_HermCount, y = pollen_depo, 
                              group = Sex, color = Sex), width = 0.3, 
                              height = 0.025, alpha = 0.5) +
  labs(x = "Hermaphrodite Neighbors", y = "", color = "Sex")+
  theme_classic()+
  scale_color_manual(values = c("#7A378B", "#66CD00")) +
  scale_fill_manual(values = c("#7A378B", "#66CD00")) +
  theme(legend.position = "none"))


ggsave(pollen_SR_plot, file = "./Figures/Pollen_Depo2.png", dpi = 300, width = 6, height = 5)


(ggplot(data = stigma_all, aes(x = Sex, y = Pollen_Number_1, fill = Sex)) +
  geom_violin(alpha = 0.25) +
  geom_boxplot(width = 0.1) +
  theme_classic()+  
  labs(y = "Pollen Number", x = "") +
  scale_fill_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks = element_blank()))


```


### Pollen Deposition Count given pollen was deposited on the stigma
```{r}
# Pollen number
pollen1 <- stigma_all %>% filter(pollen_depo == 1) %>% 
  mutate(Sex = if_else(Sex == "F", "Female", "Hermaphrodite"))

q2_pollen_num_SL.m <- glmer.nb(Pollen_Number_1 ~ (Stigma_Length + true_HermCount) * Sex + Population + true_FemCount + (1|Plant.ID), data = pollen1, verbose = TRUE)

summary(q2_pollen_num_SL.m)
r.squaredGLMM(q2_pollen_num_SL.m)
Anova(q2_pollen_num_SL.m)


RE_pollen_num_SL.m <- glm(Pollen_Number_1 ~ (Stigma_Length + true_HermCount) * Sex + Population + true_FemCount, data = pollen1, family = "poisson")
anova(q2_pollen_num_SL.m, RE_pollen_num_SL.m)



# Check Residuals
qqPlot(resid(q2_pollen_num_SL.m))

#Check Overdispersion
check_overdispersion(q2_pollen_num_SL.m)

# Model diagnostics
polnum_res <- simulateResiduals(q2_pollen_num_SL.m)
plot(polnum_res)


# Make Plots
predict <- ggpredict(q2_pollen_num_SL.m, terms = c("Stigma_Length", "Sex"))

(pollen_stig_plot2 <- ggplot(data = predict, aes(x=x, y=predicted)) +
  geom_smooth(size = 1, se = FALSE, aes(color = group)) +
  geom_ribbon(aes(x=x, ymin = conf.low, ymax = conf.high, group = group), alpha = 0.2) +
  geom_jitter(data=pollen1, aes(x = Stigma_Length, y = Pollen_Number_1, 
                           group = Sex, color = Sex), 
              width = 0.25, alpha = 0.5) +
  labs(x = "Stigma Length (mm)", y = "Pollen Number\n when Deposited", color = "Sex")+
  theme_classic()+
  scale_y_continuous(trans = "log", labels = label_number(accuracy = 0.01)) +
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "right"))

ggsave(pollen_stig_plot2, file = "./Figures/Pollen_Depo2.png", dpi = 300, width = 6, height = 5)

```


Pollen Deposition multi-panel figure
```{r}
(pollenDepo_plot <- ggarrange(pollen_stig_plot1, pollen_SR_plot, pollen_stig_plot2, ncol = 3, nrow = 1, 
                              labels = c("A", "B", "C"), 
                              common.legend = TRUE, legend = "bottom"))

ggsave(pollenDepo_plot, file = "./Figures/Pollen_Depo.png", width = 8, height = 4, units = "in", dpi = 300, bg = "white")
```


Plant Density
```{r}

mean_dens <- stigma_all %>% 
  group_by(Population) %>% 
  summarise(dens_mean = mean(density),
            n = n(),
            dens_se = sd(density) / (sqrt(n)))

(density_plot2 <- ggplot(data = mean_dens, aes(x = Population, y = dens_mean)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = dens_mean - dens_se, ymax = dens_mean + dens_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Population", y = "Density") +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position="none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))


mean_MSR <- stigma_all %>% 
  filter(!micro_SR == "NaN") %>% 
  group_by(Population) %>% 
  summarise(MSR_mean = mean(micro_SR),
            n = n(),
            MSR_se = sd(micro_SR) / (sqrt(n)))

(density_plot2 <- ggplot(data = mean_MSR, aes(x = Population, y = MSR_mean)) +
  geom_bar(stat = "summary", fun = "mean", position = position_dodge()) +
  geom_errorbar(aes(ymin = MSR_mean - MSR_se, ymax = MSR_mean + MSR_se), 
                position = position_dodge(0.9), width = 0.25) +
  labs(x = "Population", y = "Micro Sex Ratio") +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position="none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))


# Average density and hermaphrodite number across individual plants
mean_ID <- stigma_all %>% 
  group_by(Population, Sex, Plant.ID) %>% 
  summarise(mean_density = mean(density),
            mean_herm = mean(true_HermCount),
            mean_SR = mean(micro_SR))

(density_plot1 <- ggplot(stigma_all, aes(x = density, y = pollen_depo, group = Sex, color = Sex)) +
  geom_jitter(width = 0.3, height = 0.025, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(c("binomial"))) +
  labs(x = "Density", y = "Probability of\n Pollen Deposition")+
  theme_classic()+
  facet_wrap(vars(Population), scales = "free")+
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "none"))

(density_plot1 <- ggplot(mean_ID, aes(x = mean_density, y = mean_SR, group = Sex, color = Sex)) +
  geom_jitter(height = 0.1, alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "poisson")) +
  labs(x = "Micro Density", y = "Micro Sex Ratio")+
  theme_classic()+
  facet_wrap(vars(Population), scales = "free")+
  scale_color_manual(values = c("#7A378B", "#66CD00"))+
  theme(legend.position = "none"))


ggarrange(density_plot2, density_plot1, nrow = 1, ncol = 2, labels = c("A", "B"), widths = c(0.5, 1))


```



